---
title: "Online Appendix"
output: pdf_document
---
\begin{table}[!htbp] \centering 
  \*{Table A1: List of Top Travel Sponsors by Total Trips Given per Congress (2007-2017)} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}} lllc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & Travel Sponsor & Trips \\ 
\hline \\[-1.8ex] 
 & Congressional Institute & 370.8 \\ 
 & American Israel Education Foundation & 144.8 \\ 
 & Aspen Institute & 107.6 \\ 
 & Heritage Foundation & 87.2 \\ 
 & Humpty Dumpty Institute & 45.8 \\ 
 & Consumer Electronics Association & 44.8 \\ 
 & Partnership for a Secure America & 37 \\ 
 & Information Technology and Innovation Foundation & 34.4 \\ 
 & Third Way & 31.4 \\ 
 & German Marshall Fund of the United States & 28.8 \\ 
 & Turkish Coalition of America & 28.8 \\ 
 & U.S. Association of Former Members of Congress & 28.4 \\ 
 & Progressive Congress & 24.8 \\ 
 & Ripon Society and The Franklin Center For Global Policy Exchange & 23 \\ 
 & United Nations Foundation & 23 \\ 
 & Congressional Black Caucus Institute & 22.4 \\ 
 & George Mason University & 19.6 \\ 
 & American Exploration and Production Council & 16.6 \\ 
 & Alliance for Health Reform & 16.2 \\ 
 & Everglades Foundation & 16 \\ 
 & Woodrow Wilson Center for Scholars & 15 \\ 
 & International Conservation Caucus Foundation & 13.8 \\ 
 & Depository Trust and Clearing Corporation & 13.2 \\ 
 & National Cable and Telecommunications Association & 12.6 \\ 
 & Club for Growth & 12.4 \\ 
 & Massachusetts Institute of Technology & 12.2 \\ 
 & American Youth Policy Forum & 12 \\ 
 & National Association of Broadcasters & 11.8 \\ 
 & Center for Democracy in the Americas & 11.2 \\ 
 & American Enterprise Institute & 10.8 \\ 
 & Turkic American Federation of Midwest & 10.6 \\ 
 & Louisiana Sugar Cane Foundation & 10.4 \\ 
 & Internet Association & 9.6 \\ 
 & Iowa Renewable Fuels Association & 9.2 \\ 
 & ACT The App Association & 9 \\ 
 & Foundation for Nuclear Studies & 9 \\ 
 & International Committee of the Red Cross & 8.2 \\ 
 & Center Forward & 8 \\ 
 & ABC News & 7.8 \\ 
 & Google, Inc. & 7.6 \\ 
 & Main Street Partnership & 7.6 \\ 
 & J Street Education Fund & 7.4 \\ 
 & Federal Home Loan Bank of San Francisco & 7.2 \\ 
 & National Parks Conservation Association & 6.8 \\ 
 & Bertelsmann Foundation & 6.4 \\ 
 & Federal Home Loan Bank of Atlanta & 6.4 \\ 
 & Postsecondary National Policy Institute & 6.4 \\ 
 & Progressive Policy Institute & 6.2 \\ 
 & BSA Business Software Alliance, Inc. & 6 \\ 
 & Defense Forum Foundation & 6 \\ 
 & Republican Main Street Partnership & 6 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table} 


\begin{table}[!htbp] \centering
  \*{Table A2: Effects on Total Number of Gifted Trips - 110th-114th Congresses}
  \label{}
\begin{tabular}{@{\extracolsep{5pt}}lc}
\\[-1.8ex]\hline
\hline \\[-1.8ex]
\\[-1.8ex] & Coefficient \\
\hline \\[-1.8ex]
 Ideological Extremity & 0.348$^{*}$ \\
  & (0.142) \\
 Democrat & $-$1.886$^{***}$ \\
  & (0.276) \\
 Win Percentage & 0.005$^{**}$ \\
  & (0.001) \\
 Ranking Member & 0.627$^{***}$ \\
  & (0.132) \\
 Seniority & 0.008 \\
  & (0.005) \\
 Committee Chair & 0.761$^{***}$ \\
  & (0.082) \\
 Party Leader & 0.755$^{***}$ \\
  & (0.129) \\
 114th Congress & 0.850$^{***}$ \\
  & (0.062) \\
 113th Congress & 0.776$^{***}$ \\
  & (0.061) \\
 112th Congress & 0.602$^{***}$ \\
  & (0.061) \\
 111th Congress & 0.407$^{***}$ \\
  & (0.061) \\
 Ideological Extremity x Democrat & 1.698$^{***}$ \\
  & (0.270) \\
 Ranking Member x Democrat & $-$0.490$^{**}$ \\
  & (0.171) \\
 Constant & 0.224 \\
  & (0.179) \\
\hline \\[-1.8ex]
Observations & 2,180 \\
Log Likelihood & $-$5,478.676 \\
$\theta$ & 2.129$^{***}$  (0.104) \\
\hline
\hline \\[-1.8ex]
\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.05; $^{**}$p$<$0.01; $^{***}$p$<$0.001} \\
 & \multicolumn{1}{r}{Standard errors reported in parentheses.} \\
\end{tabular}
\end{table}


```{r, echo = F, message = F}
library(ggplot2)
library(MASS)
giftdata <- read.csv(file = "110-114Congresses.csv", header = TRUE, stringsAsFactors = FALSE)
ggplot(data = giftdata, aes(x=trips)) + geom_histogram(color="black", fill="black", alpha=0.4) + theme_classic() + labs(x="Number of Trips", y="Number of Members") + 
      ggtitle("Figure A1: Histogram of Trips per Congress (2007-2017)")
```

```{r, echo = F, message = F}
library(RColorBrewer)
giftdata <- read.csv(file = "110-114Congresses.csv", header = TRUE, stringsAsFactors = FALSE)
#ggplot(data = giftdata, aes(x = trips, fill = as.factor(party))) + geom_histogram(alpha=0.8, position="stack") + theme_classic() + scale_fill_manual(name =c("Legend"), values=c("blue", "red"), labels=c("100"="Democrats", "200"="Republicans")) + labs(x="Number of Trips", y="Number of Members")
ggplot(data = giftdata, aes(x = trips, fill = as.factor(party))) + geom_histogram(alpha=0.8, position="stack") + theme_classic() + scale_fill_manual(name =c("Legend"), values=c("black", "grey"), labels=c("100"="Democrats", "200"="Republicans")) + labs(x="Number of Trips", y="Number of Members") +
      ggtitle("Figure A2: Histogram of Trips per Congress (2007-2017) by Party")
```


```{r, echo = F, message = F}
library(rio)
library(tidyverse)
bb <- import("110-4gt_foreign_staff.csv")
bb <- bb[bb$FilingType == "Original",] # keep only "Original" filings 
# proportion of trips by member over time	
bb %>% ggplot(aes(factor(MemberTrip))) + geom_bar(aes(fill = factor(cong)), position = "dodge") + labs(x="Trip Attendee", y="Count of Trips Taken") + scale_x_discrete(labels=c("0" = "Staffer", "1" = "Member")) + scale_fill_discrete(name="Congress") + theme_classic() +
      ggtitle("Figure A3: Count of Trips Taken by Attendee (2007-2017)")
```

```{r, echo = F, message = F}
bb <- import("110-4gt_foreign_staff.csv")
bb <- bb[bb$FilingType == "Original",] # keep only "Original" filings 
# proportion of trips by member over time	
# count of trips abroad over time
bb %>% ggplot(aes(factor(Foreign))) + geom_bar(aes(fill = factor(cong)), position = "dodge") + labs(x="Trip Destination", y="Count of Trips Taken") + scale_x_discrete(labels=c("0" = "Domestic", "1" = "Foreign")) + scale_fill_discrete(name="Congress") + theme_classic() +
      ggtitle("Figure A4: Count of Trips Taken, by Destination (2007-2017)")
```


```{r, echo = F, message = F}
bb <- import("110-4gt_foreign_staff.csv")
bb <- bb[bb$FilingType == "Original",] # keep only "Original" filings 
# proportion of trips by member over time	
# count of trips abroad over time
bb %>%  ggplot(aes(x = cong, fill = factor(Foreign))) + geom_bar(position = "fill") + labs(y = "Proportion of Trips ",
      x = "Congress") + scale_fill_discrete(name = "Destination", labels = c("Domestic", "Foreign")) + ggtitle("Figure A5: Proportion of Foreign versus Domestic Trips (2007-2017)")
```

```{r, echo = F, message = F}
bb <- import("110-4gt_foreign_staff.csv")
bb <- bb[bb$FilingType == "Original",] # keep only "Original" filings 
# proportion of trips by member over time	
# count of trips abroad over time
bb %>% filter(Foreign == 0) %>% ggplot(aes(x = cong, fill = factor(MemberTrip))) + geom_bar(position = "fill") + labs(y = "Percentage of Domestic Trips",
      x = "Congress") + scale_fill_discrete(name = "Traveler", labels = c("Staff", "Members")) + ggtitle("Figure A6: Percentage of Domestic Trips Taken by Staff and Members")
```

```{r, echo = F, message = F}
bb <- import("110-4gt_foreign_staff.csv")
bb <- bb[bb$FilingType == "Original",] # keep only "Original" filings 
# proportion of trips by member over time	
# count of trips abroad over time
bb %>% filter(Foreign == 1) %>% ggplot(aes(x = cong, fill = factor(MemberTrip))) + geom_bar(position = "fill") + labs(y = "Percentage of Foreign Trips",
      x = "Congress") + scale_fill_discrete(name = "Traveler", labels = c("Staff", "Members")) + ggtitle("Figure A7: Percentage of Foreign Trips Taken by Staff and Members")
```


