---
title: 'Gift Travel in the U.S. House of Representatives'
author: "Philip R. Moniz & Zachary A. McGee"
date: \today
output:
  pdf_document: default
  word_document: default
bibliography: /Users/philipmoniz/Data/allreferences.bib
tables: true
linestretch: 2
fontsize: 12pt
---
\abstract{XXX REVISE WITH NEW DESCRIPTIVES The relationship between interest groups and members of Congress plays out in many ways, some of which have received great scholarly attention while others have gone relatively unnoticed. We present a study highlighting the gifted trips that members take at the invitation and reimbursement of nongovernmental organizations. We introduce this "gift travel" as a tool that interest groups use to influence and exchange information with members. We analyze all gift-travel reports provided to the Clerk of the House from 2007 to 2017. Members reported spending 42,388 days engaged in gift travel during that time, with each member traveling an average 19 days per biennium. We find that interest groups target powerful members over the rank and file; and that more ideologically extreme members are more likely to go on gifted trips. Our analysis opens a new avenue for research on the interaction between members of Congress and interest groups.}

\newpage

Gift travel is an important, but understudied, form of representative behavior. *Gift travel* occurs when a member, or one of her staff, goes on an expense-paid trip sponsored by a non-governmental organization, such as a trade association, think tank, cable channel, or university. Going on an expense-paid trip, often over the course of several days, compared to accepting one of hundreds of campaign contributions, is more meaningful for a relationship between a member and an interest group. Time may be a legislator's most important resource [@Fenno1978, 34]. When members go on these sponsored trips, they must report it to the Clerk of the House.[^1] Members reported spending 42,388 days on 10,364  gift trips over the 2007-2017 period, with each member traveling an average 19 days per biennium.

[^1]: According to Rule XXV, clause 5 of the Rules of the House of Representatives, members must disclose reimbursement for such travel within 15 days of return [@Wickham2015]. The Clerk of the House makes a report of these disclosures public on its website.

Our argument is built upon the scholarship that has failed to find a link between campaign contributions and roll-call votes [@Welch1982; @Wright1990]. Moreover, we seek to build upon scholarship that has argued for a more nuanced relationship between interest groups and members, like contributions timed before key votes or committee markups [@Stratmann1998; @Hall1990], contributions in exchange for meetings with members [@Langbein1986], and the provision of information or services to members' offices [@Hall2006].

This nuanced approach to interest group and member behavior is consistent with previous research on privately sponsored travel. @Rosenson2009 argues that trip sponsors may have multiple goals in sending members on trips and that members have various reasons for accepting their invitations. She finds that institutional power, ideology, and seniority all play a role in predicting trips by members or their staffs [@Rosenson2009]. We examine a broader period of activity than Rosenson, though only for House members, and utilize data reported directly to the Clerk of the House instead of to a third party.

While money is generally seen as the most important resource to many politicos, we argue that the scarcity of time on Capitol Hill is of far greater importance due to its scarcity. Any time spent on gifted trips during recess is time not spent in the district;[^2] and, any time spent while the House is in session needs to be coordinated with leadership to ensure no important votes will be missed. Put simply, gift travel requires much more activity from a member than simply receiving a check. In turn, we argue that interest groups provide members with gift travel as an attempt to buy face-to-face access, reinforce relationships, and support their policy-related activity [@Hall2006].

[^2]: Note that occasionally gifted trips occur with state delegations, which may entail members visiting their own districts. Most trips occur outside of members' districts.

Despite a lack of scholarly attention, gift travel has already been highlighted by the popular media as potentially corrupting. For example, at the end of May 2013, ten members of Congress, along with thirty-two staffers and dozens of state legislators, traveled to Baku, Azerbaijan. Gathering on the shore of the Caspian Sea, they took part in an all-expense-paid conference and cultural visit. The members and their staff listened to speeches given by the president of Azerbaijan, three former advisers to President Obama, and attended at least three briefings pertaining to the country's state-owned oil company. The trip sparked controversy when it was reported that the Azerbaijan-affiliated nonprofits that sponsored the travel had used money originating from a state agent, the very same state-owned oil company that had held information sessions during the conference [@Tucker2014].
<!--
The representatives, many of whom brought along their spouses, also partook in local festivities, such as a fireworks show for Republic Day of Azerbaijan, and a tour of the Old City.

As per House rules, the members had all received approval from the House Ethics Committee before going to Baku, but, upon returning to the United States, they failed to report the foreign and corporate sponsorship they witnessed there [@Tucker2014]. The *Washington Post* speculated that the trip, and the courtship of which it was a part, may have played a role in a few of the members' decisions to sponsor amendments that exempted an Azerbaijani pipeline project from a sanctions bill that was under consideration at the time [@Choma2015; @Higham2015]. The Office of Congressional Ethics ultimately recommended to the House Ethics Committee that the investigation into nine members who violated House code and federal law be further reviewed, and it was handed off to the Department of Justice [@OCE2015].

While it is legal for nongovernmental organizations to pay for members to go on such excursions, members are forbidden from accepting travel offers from foreign countries or corporations that employ U.S. lobbyists, and members may not meet with lobbyists at any time during their travel [@Wickham2015]. --->

The Baku trip in particular highlights the potential for gift travel to be gamed by the sponsors, the laxness of the self-reporting system, and the difficulty in connecting what goes on during these trips with legislators' preferences and behavior. While this particular trip was unusual because it may have involved breaking federal law (e.g., the Emoluments Clause), in many other ways it was an ordinary instance of gift travel. Members were invited by a nonprofit to listen to speeches in and tour around a foreign country. The speeches, briefings, and mingling were all a part of what a member typically experiences on a gift-travel trip.
<!--
Rule XXV is also clear that no such gift travel can be paid for by a registered lobbyist or by the agent of a foreign principal, and neither can a registered lobbyist or agent of a foreign principal be present at any time during the trip. There are a few exceptions where members of Congress may have their travel paid for by foreign governments. These exceptions are usually when foreign governments pay for in-country expenses or travel for members visiting the sponsoring country. There are limitations for how long these foreign-government-paid trips may be, and oftentimes these trips must be pre-approved by the relevant committee.
--->

Learning about gift travel behavior informs us about how members spend their valuable time and resources on an unseen realm of information exchange sponsored by groups seeking influence in the policy process. This paper provides an important systematic examination of this specific kind of travel behavior while also attempting to better understand some of the basic dynamics between these members and the interest groups sponsoring their trips.

We theorize that sponsoring organizations seek short-term policy influence, information exchange, and the opportunity to have the member's attention and build a long-term relationship (i.e., access to the member). Therefore, we conjecture that groups target members who are strategically positioned to influence policy. Such members will likely be among the party leadership [@Cox2005; @Rosenson2009; @Curry2015], electorally safe [@Grimmer2013], senior [@Snyder1992; @Rosenson2009], and relatively moderate ideologically [@Alduncin2017; @Krehbiel1998]. Sponsors are typically specialized organizations, like trade associations or think tanks, and must balance their preferences for power, policy-interest, and feasibility. While everyone might want to get the ear of the Speaker, only the most resourceful sponsors are apt to do so. Others must take what they can get, and use their finances wisely [@Barber2017].

We present three major findings. First, party leaders, committee chairs, and ranking members travel much more than the rank and file, which is consistent with Rosenstone's data from 2001-2004. Second, seniority is not a significant predictor of the number of gift travel trips a member goes on, and electoral safety has only a trivial effect. Third, and unexpectedly, more ideologically extreme members travel more than their moderate colleagues. We will now turn to our data and detail what we know about gift travel. We close the paper with a more detailed discussion of our findings, the implications thereof, and suggestions for avenues of future research on gift travel and corruption in Congress.

<!--
# Interest Groups and CODELs

Members of Congress and interest groups have a dynamic relationship. Because they are engaged in a mutually beneficial give-and-take, the American public is regularly suspicious about the potential for corruption between these groups and their representatives. Suspicious of these relationships too, political scientists have investigated how interest groups, corporations, and think tanks---and their respective PACs---attempt to influence policymakers. Scholars have not found much direct evidence of exogenous actors directly "buying" members votes [@Welch1982; @Wright1990]. Contributions that are timed correctly, such as before critical votes, have given scholars pause [@Stratmann1998]. And, certain groups seem to invest in members long-term [@Snyder1992].

A more nuanced type of influence is more likely. Hall and Wayman [-@Hall1990] argue that contributions lead to less measurable changes, like shifts in the content of bills. It is also possible that interest groups provide critical information or services that make the lives of already overwhelmed legislators easier [@Hall2006]. Langbein [-@Langbein1986] argues that money buys access to members of Congress and, using predicted probabilities, finds that a PAC would need to contribute approximately \$72,000 for one hour with a member. Langbein also finds that the mean contribution in the 1975-1976 election cycle was \\$28,360, which yielded about 35 minutes of private meeting time with a member. There are two critical takeaways from these scholarly works. First, similar to Hall and Wayman and Hall and Deardorff, we expect a nuanced type of influence is likely at work with gift travel. And, second, gifted trips are much more taxing than a 35 minute meeting, which further buttresses the need for attention to these trips.

The study of when and where members of Congress travel is not new. For instance, scholars have investigated where, how often, for how long, and with whom, members travel abroad as part of Congressional Delegations, or CODELs in D.C. argot [see for example @Alduncin2014; @Alduncin2017]. Some CODELs are partisan, others are bipartisan, but they are usually conducted in groups, presumably for the purpose of learning something valuable to their jobs as legislators.[^3] Alduncin et al. [-@Alduncin2014] find that trips abroad are getting shorter and, in general, members are spending less time together. With members spending less time together, the authors argue that the social fabric within the institution is fraying. Alduncin, Parker, and Theriault [-@Alduncin2017, 1] find a still fraying social fabric and argue that bipartisan foreign travel has become "a victim of the partisan war waging in Congress." Their conclusion was drawn from the bleak realities of their findings, which were that (among other things) extremely conservative House Republicans have become much more likely to travel with only co-partisans. The effects are similar, but of a lesser magnitude, for moderate Republicans.

[^3]: CODELs differ from gift travel in important ways. For general CODEL trips abroad, when members want to travel they must first request permission and funding from the parent chamber or relevant committee. Gift travel, however, requires a sponsoring organization and therefore is much more susceptible--theoretically--to quid pro quo corruption. Another important difference is that members in CODELs can ask fellow members if they would like to participate in a delegation trip. Again, gift travel differs in that the sponsoring organization selects who travels. With the power to target individual members in the hands of the sponsors, it is important to understand this potential mechanism of influence.

We will rely on the literature on foreign travel among members of Congress to inform our hypotheses about gift travel, since foreign travel is the nearest thing to gift travel that scholars have studied. The key difference to keep in mind is that delegation and committee travel are the product of members' initiative while gift travel starts, at least in theory, with the sponsor.

# The Causes of Gift Travel

Gifts imply relationships. Every gift-giving situation involves a giver and a recipient. Gifts are usually given as an expression of love, respect, or appreciation, and while they are not given with the expectation of reimbursement, they can be given with the expectation of reciprocity [@Graeber2011]. The relevant question here is: Which members are most likely to reciprocate a sponsor's gift? Reciprocation in this situation would mean that the member had improved the chances that the sponsor's policy preferences became law. Gift travel is not a direct campaign contribution, and therefore it may be perceived as a less "direct" source of influence. But, since gift travel is a relatively hidden activity (from the public's perspective), it may be a powerful avenue of influence for sponsors of travel.

We posit that sponsors are organizations that are looking for short-term influence on policymaking, and sending members to conferences and on fact-finding missions is an attempt to "educate" them, and be "educated" in return, in light of that purpose. Sponsors are strategic actors and will not waste their gift resources on members who cannot or will not improve their chances of influencing policymaking.

*Power hypothesis* Members who have more power, such as party leaders and committee chairs, are the first place to look for targets of gift travel. As powerful members, it would make sense for them, ceteris paribus, to receive more invitations and to go on more gift journeys than less powerful members. Influencing members in leadership positions means influencing the legislative agenda, especially in the form of negative agenda control wherein leaders can tilt policymaking in favor of the status quo [@Cox2005]. Leadership is operationalized in three different ways. We code for committee chairs, ranking members and party leaders, where party leaders are the Speaker, the majority or minority leader, a whip, or the chair of either the Republican or Democratic caucus.

*Seniority hypothesis* As Alduncin, Parker, and Theriault [-@Alduncin2017] point out, senior members may also be more likely to shift their attention toward legislation and policymaking, so there may be some causation going in the other direction; that is, senior members may cultivate relationships with travel-gifting interest groups because they want to learn about policy, or they want information gains from those interest groups [@Hall2006].

*Safety hypothesis* Members with large margins of victory, because they are often from ideologically aligned districts, are more likely to pursue national-level policy issues [@Grimmer2013a]. Therefore, we should also expect that electorally safer members have more latitude to build relationships with travel-gifting groups. These safer members should then take more trips at these groups' expense. Note that we adjusted the win percentage observations for those members in California who ran against copartisans in the general election because of California's unique primary system. Instead of being given 100% of the vote share, Democrats who defeated other Democrats, for example, were tallied as having won with whatever percentage they got in the general election. This adjustment corrects for what may have been an overestimate of the number of unopposed members.

*Ideology hypothesis* As for the direct effect of members' political ideology, there is an interesting difference in how ideology may come into play in foreign travel as opposed to gift travel. @Alduncin2017 speculate that more ideologically extreme members would tend to travel abroad less because they would be less inclined to think that they had something to learn from how foreign countries do things. They report that conservative Republicans have always been less likely to travel. The authors further speculate that, because foreign travel often entails flying with members of the other party, ideologically extreme members will travel less than more moderate members. To create our measure of ideological extremity, we start with the Common Space DW-NOMINATE scores, and then calculate the distance, in absolute value, of each member from the opposing party's mean.

The first speculation applies partially to gift travel because some sponsored trips are to foreign countries for the purpose of learning about social and political life abroad; other trips, however, keep members in the United States and can bring them to ideologically charged events, such as those held by think tanks like the Heritage Foundation. Therefore, because gift travel may be more conducive to ideology-affirming experiences than foreign travel, ideological members may be no different than moderate members in their quantity of travel.

Whether or not ideological members are advantaged over moderate members depends on the sponsor organizations and their motives. If sponsors as a group are highly ideological, and they seek out likeminded legislators in order to give them information subsidies [@Hall2006], then more ideological members should travel more. Our hypothesis will remain what previous literature has found, but with the thought in mind that the sponsor-led nature of gift travel may result in different patterns than foreign travel.

The second speculation is less obviously relevant than the first to gift travel because gift travel need not be conducted as part of a group, and sponsors decide the composition of the group if there is one. Bipartisan gift travel is not unheard of. There are instances, such as the entire Indiana delegation going on a trip sponsored by a soybean farmers' trade association, where members of different parties travel together. State-delegation excursions appear to be the exception rather than the rule though. Notably, we find that sponsors seem to hand-select which members they send on trips.
--->


# Data

Our data come from reports filed to the Office of the Clerk of the U.S. House of Representatives. Every year since 2007, the Clerk has published all gift travel reports [@Dent2015, 11]. This paper analyzes these reports from the 110th through the 114th Congresses (2007-2017). These data, after cleaning, collapsing duplicate trip entries, and aggregating by member, consist of 2,180 observations, which are at the level of the member per congress. Over the course of the ten-year period for which we have data, each member, or their staff, traveled an average 19 days per congress and reported spending a total of 42,388 days (on 10,364 trips) engaged in gift travel; the average trip is about four days.

### Sponsors; or, the Givers

A glance at the list of reports quickly shows that there is not a standard or system by which members are filling out their gift-travel paperwork. After attempting to correct for typos and various names for the same organization, we found that a total of 1,466 nongovernmental sources provided reimbursement for travel to members of Congress between 2007 and 2017.[^3] Each of these organizations gave at least one gift-trip in that ten-year period, which equates to about 250 organizations per Congress, with each congressional cohort taking about 2,500 trips.

[^3]: Filing these reports is left up to the members and their staffs. It is up to them to spell the name of the sponsor correctly, use the full name or an abbreviation, and, indeed, know exactly who it is that is sponsoring the trip. Because of this, the true number of sponsors is likely slightly lower than 1,466.

We also might wonder whether travel sponsors are an egalitarian bunch, each giving roughly the same number of trips per congress, or whether the travel-sponsor universe is more accurately characterized as dominated by a few sponsors that account for the bulk of members' gift travel year after year. As it turns out, a small number of familiar names are responsible for a hefty portion of the number of trips taken each congress. Only about 4% (63 out of 1466) of the sponsoring organizations averaged at least one trip per congress, or five total in the data set. This datum would imply that only five or six dozen organizations are assuming the cost of putting members on trips as a regular part of business. The other 95% or so appear to be using gift travel only sparingly, possibly in reaction to shifts in the policy agenda or opportunities to alter the policy-content of bills [@Jones2005; @Hall1990].

The sixty-two organizations that, on average, sponsored one or more trips per congress account for 72% of the all the reported trips in our data set. The concentration of gifting behavior among a handful of sponsors is an important descriptive fact to note. Our theoretical expectation is that more powerful members will travel more often, and if the same sponsors are doing so over and over, then this makes it likely that travel sponsors are generally well-funded and strategic, not circumstantial or one-off givers.

To get some notion of who the big players are, let's look briefly at the top five sponsors. The most active sponsor, by far, is an organization called the Congressional Institute, which provided travel subsidies an average of 371 occasions per Congress. The Congressional Institute appears to invite great numbers of members, usually around 150 of them, to places near Washington, such as Hot Springs, Virginia. The Institute claims to advocate for congressional reform; for example, promoting the idea of a joint committee that will propose changes to rules and procedures followed in the House and Senate. This group is the same that @Rosenson2009 indicated as the top sponsor. The remaining munificent groups are the American Israel Education Foundation (146 trips per Congress), the Aspen Institute (107), the Heritage Foundation (88), and the Humpty Dumpty Institute (46). The Aspen Institute and the Heritage Foundation are think tanks; the Humpty Dumpty Institute is an international NGO; and the American Israel Education Foundation is an interest group, self-described as being part of America's pro-Israel lobby. Each of these organizations clearly has either a policy solution to offer or a policy problem it hopes to push onto the congressional agenda.

### Taking Trips

We have one primary dependent variable for our analysis: *trips*. It is a count, i.e., a sum of binary items (traveled or did not), and it is over-dispersed.[^4] Further, there is heterogeneity across individuals' probabilities of traveling. Each member of Congress does not have an equal probability of being selected to travel by a sponsoring organization. Party leaders or committee chairs are especially prone to this heterogeneity because these members hold more power or policy expertise than rank-and-file members. Therefore, we estimate a negative binomial regression using maximum likelihood. We include fixed-effects for each Congress.

[^4]: Overdispersion occurs when the observed variance is larger than the expected variance from a given model [@Collett2003]. The count is the number of separate journeys reported by each member to the Clerk of the House; each unique report counts as one trip.

Our trips variable is aggregated at the office level. Members do not go on every trip themselves. We argue this aggregation is appropriate because a member's office is instrumental to her legislative behavior [@Mayhew1974]. Moreover, the data indicate that members go on only about 30% of the trips they report. The remaining 70% of trips are attended by staffers. In fact, the proportion of trips taken by staffers, when broken down by Congress, shows that members are attending fewer and fewer trips each congressional biennium. And, even though members are attending smaller proportions of trips each year, the total number of trips reported each year continues to grow.

```{r, echo = F, message = F, fig.cap = "Count of Trips Taken by the Member (2007-2017)"}
library(rio)
library(tidyverse)
bb <- import("110-4gt_foreign_staff.csv")
bb <- bb[bb$FilingType == "Original",] # keep only "Original" filings 
# proportion of trips by member over time	
bb %>% ggplot(aes(factor(MemberTrip))) + geom_bar(aes(fill = factor(cong)), position = "dodge") + labs(x="Trip Attendee", y="Count of Trips Taken") + scale_x_discrete(labels=c("0" = "Staffer", "1" = "Member")) + scale_fill_discrete(name="Congress") + theme_classic()
```

Staffers are clearly playing a key role in this information exchange and should be treated as equals in our analysis (see Figure 1). While it may seem unconventional to equate members and their staffers, consider that if interest groups were not seeing the same results when staffers attend, they would likely stop offering to pay for trips for these members. Or, groups might insist the member attend and refuse to pay for a staffer. But, since we can see a clear trend in the number of trips being attended overall increasing with each Congress, we do not find this explanation feasible.

Not all members (or their staffers) go on gift travel, but most of them do. Of the 2,180 total members, 292 (13.4%) did not go on a single trip. Similarly, 253 members (11.6%) went on exactly one, 42 (11.4%) went on two, 255 (11.7%) went on three, with 4.8 trips being the mean. Figure 2 shows a histogram of the number of trips taken by all the members. The figure is heavily right-skewed (mean = 4.8, sd = 4.7, median = 4), with only 30 members going on 20 or more trips. The member to go on the most trips, Fred Upton (MI-R), went on 50 trips; he was both a committee chairman and a senior member. Louise Slaughter (NY-D), another senior member in a high-ranking committee position, though in the minority party, went on zero trips during the 114th Congress.

```{r, echo = F, message = F, fig.cap = "Histogram of Trips (2007-2017)"}
library(ggplot2)
library(MASS)
giftdata <- read.csv(file = "110-114Congresses.csv", header = TRUE, stringsAsFactors = FALSE)
ggplot(data = giftdata, aes(x=trips)) + geom_histogram(color="black", fill="black", alpha=0.4) + theme_classic() + labs(x="Number of Trips", y="Number of Members")
```

Democrats travel less often, on average, compared to Republicans (see Figure 3). The average number of trips among Democrats is 4.3, but the variance is large ($\sigma^2 = 23.7$). Republicans, on average, go on one more trip than Democrats; their average is 5.2, but again, the variance is large ($\sigma^2 = 20.3$). It may be that the difference in trips between the two sets of party members can be attributed to the varying issues on the congressional agenda and the groups tied to those issues. Put another way, groups concerned about the issues that receive disproportionate attention during the decade we are analyzing would have disproportionate incentive to send members on trips. If one side of a given issue was more actively mobilized than another it could quickly lead to partisan differences in trips taken.

```{r, echo = F, message = F, fig.cap = "Histogram of Trips per Congress (2007-2017) by Party"}
library(RColorBrewer)
giftdata <- read.csv(file = "110-114Congresses.csv", header = TRUE, stringsAsFactors = FALSE)
#ggplot(data = giftdata, aes(x = trips, fill = as.factor(party))) + geom_histogram(alpha=0.8, position="stack") + theme_classic() + scale_fill_manual(name =c("Legend"), values=c("blue", "red"), labels=c("100"="Democrats", "200"="Republicans")) + labs(x="Number of Trips", y="Number of Members")
ggplot(data = giftdata, aes(x = trips, fill = as.factor(party))) + geom_histogram(alpha=0.8, position="stack") + theme_classic() + scale_fill_manual(name =c("Legend"), values=c("black", "grey"), labels=c("100"="Democrats", "200"="Republicans")) + labs(x="Number of Trips", y="Number of Members")
```

Of course, not all trips are the same. Some trips involve foreign travel, while others entail just a quick jaunt into a state bordering the District of Columbia. Twenty-nine percent of all trips, on average, involved travel outside the United States.[^5] Figure 4 shows that, with the exception of the 114th Congress, foreign trips are growing in number, as are domestic trips. But, perhaps it is the case that members have a preference for this expense-paid foreign travel over a quick trip into Maryland or Virginia. Foreign trips are certainly more attractive in that it is more expensive to travel outside the U.S. than within it. Nevertheless, as [-@Alduncin2014] point out, members are on "a shorter leash than the generations before them, members of Congress today participate in [trips abroad] more cautiously, lest they become the issue in their next campaign" (564).

[^5]: This proportion is consistent across time with the lowest proportion being 25% foreign travel in the 110th Congress. See Figure A1 in the appendix, which details this trend.

```{r, echo = F, message = F, fig.cap = "Count of Foreign Trips Taken (2007-2017)"}
bb <- import("110-4gt_foreign_staff.csv")
bb <- bb[bb$FilingType == "Original",] # keep only "Original" filings 
# proportion of trips by member over time	
# count of trips abroad over time
bb %>% ggplot(aes(factor(Foreign))) + geom_bar(aes(fill = factor(cong)), position = "dodge") + labs(x="Trip Destination", y="Count of Trips Taken") + scale_x_discrete(labels=c("0" = "Domestic", "1" = "Foreign")) + scale_fill_discrete(name="Congress") + theme_classic()
```

As suspected, members have a clear preference for taking foreign trips instead of sending their staffers in their place (see Figure 5 and Figure 6). And, their preference has grown stronger over time. Members in the 114th Congress attended about half of the foreign trips compared to one-third of foreign trips in the 110th Congress. Let's turn now to our inferential analysis to try and get more concrete answers about the driving factors of gift travel.

<!---
```{r, echo = F, message = F, fig.cap = "Proportion of Foreign Trips Taken by Members (2007-2017)"}
bb <- import("110-4gt_foreign_staff.csv")
bb <- bb[bb$FilingType == "Original",] # keep only "Original" filings 
### Member-only trips 
# proportion of member trips taken abroad over time	
# Note the increasing percentage of foreign trips being taken by the members!
bb %>% group_by(cong) %>%
	filter(MemberTrip == 1) %>%
	summarize(average_foreign = mean(Foreign), 
		average_member = mean(MemberTrip)) %>%
	ggplot(aes(cong, average_foreign)) + geom_col(aes(fill = factor(cong))) + labs(x="Congress", y="Proportion of Foreign Trips Taken by Members") + scale_y_continuous(limits = c(0, .6)) + theme_classic() + guides(fill=FALSE)
```

```{r, echo = F, message = F, fig.cap = "Proportion of Foreign Trips Taken by Members (2007-2017)"}
bb <- import("110-4gt_foreign_staff.csv")
bb <- bb[bb$FilingType == "Original",] # keep only "Original" filings 
# proportion of STAFFER trips taken abroad over time	
bb %>% group_by(cong) %>%
  filter(MemberTrip == 0) %>%
  summarize(average_foreign = mean(Foreign), 
            average_member = mean(MemberTrip)) %>%
  ggplot(aes(cong, average_foreign)) + geom_col(aes(fill = factor(cong))) + labs(x="Congress", y="Proportion of Foreign Trips Taken by Staffers") + scale_y_continuous(limits = c(0, .6)) + theme_classic() + guides(fill=FALSE)
```
---->

```{r, echo = F, message = F, fig.cap = "Percentage of Foreign Trips Taken by Staff and Members (2007-2017)"}
bb <- import("110-4gt_foreign_staff.csv")
bb <- bb[bb$FilingType == "Original",] # keep only "Original" filings 
# proportion of trips by member over time	
# count of trips abroad over time
bb %>% filter(Foreign == 1) %>% ggplot(aes(x = cong, fill = factor(MemberTrip))) + geom_bar(position = "fill") + labs(y = "Percentage of Foreign Trips Taken",
      x = "Congress") + scale_fill_discrete(name = "Traveler", labels = c("Staff", "Members"))
```


# Results

Do members of Congress differ in how many gifted trips they go on? What characteristics separate those who travel often from those who stay in Washington or only travel to their districts? The results reported in Table 1 offer answers to these questions. As expected, members in positions of power---party leaders, committee chairs, and ranking members---on average go on significantly more gifted trips than the rank and file. The statistically significant parameter estimates for these position-of-power variables indicate that powerful members travel more, but the coefficients alone do not give us a clear idea of how many more trips per Congress they go on. For the substantive meaning of the estimates, we calculate the contribution each explanatory variable makes to the predicted number of trips, and we plot the changes in Figure 3. For instance, holding all other power variables at zero and the continuous variables, *seniority*, *win percentage*, and *ideological extremity*, at their sample means, the effect of being party leader is sizable: a party leader is predicted to go on 5.49 trips per Congress, three more trips than a rank-and-file member, an increase of 113%. The effect of being a committee chair is almost identical in size to that of being a party leader, while the effect of ranking member differs across party.

\begin{table}[!htbp] \centering
  \caption{Effects on Total Number of Gifted Trips - 110th-114th Congresses}
  \label{}
\begin{tabular}{@{\extracolsep{5pt}}lc}
\\[-1.8ex]\hline
\hline \\[-1.8ex]
\\[-1.8ex] & Count of Total Gifted Trips \\
\hline \\[-1.8ex]
 Ideological Extremity & 0.348$^{*}$ \\
  & (0.142) \\
 Democrat & $-$1.886$^{***}$ \\
  & (0.276) \\
 Win Percentage & 0.005$^{**}$ \\
  & (0.001) \\
 Ranking Member & 0.627$^{***}$ \\
  & (0.132) \\
 Seniority & 0.008 \\
  & (0.005) \\
 Committee Chair & 0.761$^{***}$ \\
  & (0.082) \\
 Party Leader & 0.755$^{***}$ \\
  & (0.129) \\
 114th Congress & 0.850$^{***}$ \\
  & (0.062) \\
 113th Congress & 0.776$^{***}$ \\
  & (0.061) \\
 112th Congress & 0.602$^{***}$ \\
  & (0.061) \\
 111th Congress & 0.407$^{***}$ \\
  & (0.061) \\
 Ideological Extremity x Democrat & 1.698$^{***}$ \\
  & (0.270) \\
 Ranking Member x Democrat & $-$0.490$^{**}$ \\
  & (0.171) \\
 Constant & 0.224 \\
  & (0.179) \\
\hline \\[-1.8ex]
Observations & 2,180 \\
Log Likelihood & $-$5,478.676 \\
$\theta$ & 2.129$^{***}$  (0.104) \\
\hline
\hline \\[-1.8ex]
\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.05; $^{**}$p$<$0.01; $^{***}$p$<$0.001} \\
 & \multicolumn{1}{r}{Standard errors reported in parentheses.} \\
\end{tabular}
\end{table}

The interactive effect of ideological extremity and party on the number of gift-travel trips members go on is the second major finding of this paper. It is important not only because the magnitude of its effect is large but also because it reveals how ideology works to attract sponsors toward members in different degrees depending on their party. The first thing to note is that ideologically extreme members are more likely than their moderate colleagues to venture out at the invitation of sponsoring organizations. The large positive effect of ideological extremity holds for members of both parties, but the size of the effect is larger for Democrats than it is for Republicans. The estimated number of trips for Republicans rises from 2.1 to 3.3 (57% increase), while the number for Democrats jumps from 0.9 to 4.8 (433% increase). So, what a Democrat may lack in committee power in the eyes of sponsors, she may make up for if her views are sufficiently liberal.

We also find some interesting null effects and observe two noteworthy trends. First, though we expected otherwise, more senior and electorally safe members are no more likely than their marginal freshman counterparts to take a trip on someone else's dime. Second, since gift travel has been reported in its current fashion, members have only gone on more and more trips per congressional term. Descriptive analysis as well as the coefficient estimates for each congress in Table 1 show that the popularity of gift travel has only increased over time. Lastly, it is important to note that, all things considered, Republicans of the rank and file go on an average 2.6 total trips per congress, which is 0.4 trips (18%) more than similar Democrats do. In other words, Republicans have been jetsetting for free more than Democrats have.

<!---
Our full model includes members from both parties $(n=2180)$, which we account for by including a variable that indicates whether a member is a Democrat or not. From the negative coefficient on our party variable we can confirm what we saw from our descriptive statistics---Democrats travel less frequently than Republicans. The remaining independent variables have positive and significant coefficients. Safer members tend to travel more, but only slightly. More ideologically extreme members travel more, contrary to our theoretical expectations. Ideological extremity has the largest effect among our explanatory variables. Before speculating too much on our ideology finding, we will see if extremity has the same effects among Democrats and Republicans. Gift travel may be an avenue for ideological groups to reward loyal members and provide them with information subsidies.
--->


\begin{table}[]
\centering
\caption{Predicted Number of Trips}
\label{}
\begin{tabular}{@{}lll@{}}
\toprule
                            & 0                 & 1                 \\ \midrule
Committee Chair             & 2.58              & 5.52              \\
                            & {[}2.33 - 2.85{]} & {[}4.62 - 6.59{]} \\
Democrat                    & 2.58              & 2.17              \\
                            & {[}2.33 - 2.85{]} & {[}1.97 - 2.39{]} \\
Party Leader                & 2.58              & 5.49              \\
                            & {[}2.33 - 2.85{]} & {[}4.20 - 7.17{]} \\
Ranking Member (Republican) & 2.58              & 4.83              \\
                            & {[}2.33 - 2.85{]} & {[}3.75 - 6.22{]} \\
Ranking Member (Democratic) & 2.17              & 2.49              \\
                            & {[}1.97 - 2.39{]} & {[}1.98 - 3.15{]} \\ \bottomrule
\multicolumn{2}{l}{\footnotesize Note: Standard errors reported in parentheses}    \\
\end{tabular}
\end{table}

```{r, echo = F, warning = F, message = F, fig.height = 5, fig.cap = "Predicted Trips Taken per Congress"}
library(dplyr)
#set up data and multiplot function
giftdata <- read.csv(file = "110-114Congresses.csv", header = TRUE, stringsAsFactors = FALSE)
finalmodel <- glm.nb(trips ~ extreme*democrat + winpct + committee*democrat + seniority + chairman + party.leader + fourteenth + thirteenth + twelfth + eleventh, data = giftdata)
multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
  library(grid)

  # Make a list from the ... arguments and plotlist
  plots <- c(list(...), plotlist)

  numPlots = length(plots)

  # If layout is NULL, then use 'cols' to determine layout
  if (is.null(layout)) {
    # Make the panel
    # ncol: Number of columns of plots
    # nrow: Number of rows needed, calculated from # of cols
    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                    ncol = cols, nrow = ceiling(numPlots/cols))
  }

 if (numPlots==1) {
    print(plots[[1]])

  } else {
    # Set up the page
    grid.newpage()
    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))

    # Make each plot, in the correct location
    for (i in 1:numPlots) {
      # Get the i,j matrix positions of the regions that contain this subplot
      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))

      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                      layout.pos.col = matchidx$col))
    }
  }
}

#predicted values
extremitydata <- data.frame(extreme = giftdata$extreme, democrat = 0, winpct = mean(giftdata$winpct), seniority = mean(giftdata$seniority), chairman = 0, committee = 0, party.leader = 0, fourteenth = 0, thirteenth = 0, twelfth = 0, eleventh = 0)
extremitydataD1 <- data.frame(extreme = giftdata$extreme, democrat = giftdata$democrat, winpct = mean(giftdata$winpct), seniority = mean(giftdata$seniority), chairman = 0, committee = 0, party.leader = 0, fourteenth = 0, thirteenth = 0, twelfth = 0, eleventh = 0)
extremitydataD1 <- filter(extremitydataD1, democrat == 1)
winpctdata <- data.frame(extreme = mean(giftdata$extreme), democrat = 0, winpct = giftdata$winpct, seniority = mean(giftdata$seniority), chairman = 0, committee = 0, party.leader = 0, fourteenth = 0, thirteenth = 0, twelfth = 0, eleventh = 0)
senioritydata <- data.frame(extreme = mean(giftdata$extreme), democrat = 0, winpct = mean(giftdata$winpct), seniority = giftdata$seniority, chairman = 0, committee = 0, party.leader = 0, fourteenth = 0, thirteenth = 0, twelfth = 0, eleventh = 0)
extremitydata$phat <- predict(finalmodel, extremitydata, type = "response")
extremitydataD1$phat <- predict(finalmodel, extremitydataD1, type = "response")
winpctdata$phat <- predict(finalmodel, winpctdata, type = "response")
senioritydata$phat <- predict(finalmodel, senioritydata, type = "response")

#prep for plots
extremitydataCI <- data.frame(extremitydata)
extremitydataCI <- cbind(extremitydataCI, predict(finalmodel, extremitydata, type = "link", se.fit = T))
extremitydataCI <- within(extremitydataCI, {
  Trips <- exp(fit)
  LL <- exp(fit - 1.96 * se.fit)
  UL <- exp(fit + 1.96 * se.fit)})

extremitydataD1CI <- data.frame(extremitydataD1)
extremitydataD1CI <- cbind(extremitydataD1CI, predict(finalmodel, extremitydataD1, type = "link", se.fit = T))
extremitydataD1CI <- within(extremitydataD1CI, {
  Trips <- exp(fit)
  LL <- exp(fit - 1.96 * se.fit)
  UL <- exp(fit + 1.96 * se.fit)})

winpctdataCI <- data.frame(winpctdata)
winpctdataCI <- cbind(winpctdataCI, predict(finalmodel, winpctdata, type = "link", se.fit = T))
winpctdataCI <- within(winpctdataCI, {
  Trips <- exp(fit)
  LL <- exp(fit - 1.96 * se.fit)
  UL <- exp(fit + 1.96 * se.fit)})

senioritydataCI <- data.frame(senioritydata)
senioritydataCI <- cbind(senioritydataCI, predict(finalmodel, senioritydata, type = "link", se.fit = T))
senioritydataCI <- within(senioritydataCI, {
  Trips <- exp(fit)
  LL <- exp(fit - 1.96 * se.fit)
  UL <- exp(fit + 1.96 * se.fit)})

#plots
mypalette <- brewer.pal(3,"Greys")
p1 <- ggplot(extremitydataCI, aes(extreme, Trips)) +
  geom_ribbon(aes(ymin = LL, ymax = UL, fill = democrat), alpha = .25) +
  geom_line(aes(colour = committee), size = 1) +
  labs(x = "Ideological Extremity", y = "Predicted Trips: Republicans") + guides(colour=FALSE, fill=FALSE) + scale_fill_distiller(palette = mypalette, type = "seq") + scale_color_distiller(palette = mypalette, type = "seq") + theme_classic()
p2 <- ggplot(extremitydataD1CI, aes(extreme, Trips)) +
  geom_ribbon(aes(ymin = LL, ymax = UL, fill = chairman), alpha = .25) +
  geom_line(aes(colour = party.leader), size = 1) +
  labs(x = "Ideological Extremity", y = "Predicted Trips: Democrats") + guides(colour=FALSE, fill=FALSE) + scale_fill_distiller(palette = mypalette, type = "seq") + scale_color_distiller(palette = mypalette, type = "seq") + theme_classic()
p3 <- ggplot(winpctdataCI, aes(winpct, Trips)) +
  geom_ribbon(aes(ymin = LL, ymax = UL, fill = committee), alpha = .25) +
  geom_line(aes(colour = committee), size = 1) +
  labs(x = "Win Percentage", y = "Predicted Trips") + guides(colour=FALSE, fill=FALSE) + scale_fill_distiller(palette = mypalette, type = "seq") + scale_color_distiller(palette = mypalette, type = "seq") + theme_classic()
p4 <- ggplot(senioritydataCI, aes(seniority, Trips)) +
  geom_ribbon(aes(ymin = LL, ymax = UL, fill = fourteenth), alpha = .25) +
  geom_line(aes(colour = fourteenth), size = 1) +
  labs(x = "Terms Served in the House", y = "Predicted Trips") + guides(colour=FALSE, fill=FALSE) + scale_fill_distiller(palette = mypalette, type = "seq") + scale_color_distiller(palette = mypalette, type = "seq") + theme_classic()

multiplot(p1, p3, p2, p4, cols=2)
```

# Discussion

We have modeled the gift-travel behavior of members of Congress as a function of their party, their time spent in office, the safeness of their seat, their role as either leader or rank and file, committee leadership, and ideological extremity (or the degree to which they vote with their party and not with the other). In the aim of parsimony, we have estimated a single model for both parties while measuring the effect of party and including interaction terms for the relationships that were statistically significant. The most important of these was the interactive effect of party on ideological extremity. Our results were surprising in two ways. First, far from being a damper on travel, ideological extremity was found to be a catalyst for more trip-taking. Second, its catalyzing effect was sharply pronounced for Democratic members, the most ideologically extreme of whom were estimated to travel over 400% more per Congress than the moderate. Why this should be so is not immediately obvious. The logic of rank-and-file members retaining influence by banding together via intraparty organizations provides some support here [@BlochRubin2017].

The specific targeting of powerful members (i.e. party leaders, committee chairs, and ranking members) indicates, at minimum, that more research needs to be done on the mechanism of gift travel. If possible, an explication of what types of groups sponsor any gift travel at all and a closer look at activity within the U.S. House following trips would shed light on any question of quid pro quo corruption from these excursions.

Furthermore, in line with scholarship regarding the travel of members via Congressional Delegations (CODELs) [@Alduncin2014; @Alduncin2017], scholars could examine who travels with whom and how often. Using what the Clerk of the House provides, future research could work to determine which members were visiting the same locations at the same times, and use this information to investigate how member-level attributes relate to the partisan nature of their gift-travel behavior. Many trips gifted during the congresses analyzed here involved members traveling together, and it is possible that partisan polarization may affect gift travel in ways similar to CODELs.

Future scholarship on member travel should also try to better specify the relationship between sponsors and members. A measure of sponsor ideological similarity would go a good ways in specifying the relationship, as would a more nuanced coding of the committee-related variables. Like sophisticated donors, sponsors may also target the committees most relevant to their policy goals, or ones ideologically similar to them [@Barber2017].  Our analysis speaks to who travels and how much, but future work should investigate whether those who travel more do so because they receive trips from a wide variety of sponsors or because they are given trips again and again by the same big organizations.

One final note is that all trips are not the same, and what we have modeled here is a mere count of the quantity of trips taken by members of Congress. Some trips are domestic, others are overseas; some trips are a day long, others are a week long; some are taken alone, others are experienced in groups. The varieties of trip offer us several more questions we could ask about what these excursions mean.

Gift travel is an overlooked aspect of members' relationships with interest groups and non-governmental organizations. Many questions remain unanswered. How does gift travel change over extended periods of time? What is it good for? Researchers should appreciate the potentially important things we have to learn from this unusual form of documented lobbying and travel, and we hope to work toward answering these questions in the near future.

# Appendix
[XXX table of the 62 organizations along with how many trips they sponsored]

```{r, echo = F, message = F, fig.cap = "Proportion of Foreign Trips Taken (2007-2017)"}
bb <- import("110-4gt_foreign_staff.csv")
bb <- bb[bb$FilingType == "Original",] # keep only "Original" filings 
# proportion of trips abroad over time
bb %>% group_by(cong) %>% 
	summarize(average_foreign = mean(Foreign), 
		average_member = mean(MemberTrip)) %>%
	ggplot(aes(cong, average_foreign)) + geom_col(aes(fill = factor(cong)), show.legend = F) + scale_y_continuous(limits = c(0, .5)) + theme_classic() + labs(x="Congress", y="Average Proportion of Trips Taken Abroad") + guides(fill=FALSE)
```

# References
