---
title: 'Gift Travel in the U.S. House of Representatives'
author: "Philip R. Moniz & Zachary A. McGee"
date: \today
output:
  pdf_document: default
  word_document: default
bibliography: /Users/philipmoniz/Documents/Scholastic Scribblings/my_library.bib
tables: true
---
\abstract{The relationship between interest groups and members of Congress plays out in many ways, some of which have received great scholarly attention while others have gone relatively unnoticed. We present a study of the trips that members go on at the invitation and reimbursement of nongovernmental organizations. We introduce this "gift travel" as a tool that interest groups use to influence and exchange information with members. Since 2007, Congressional rules have required members to report all gifted travel, and we analyze all reports from 2007 to 2017. We have to big findings: interest groups target powerful members, committee chairs and ranking members, over the rank and file; and more ideologically extreme members are no less likely than their moderate counterparts to go on gifted trips. The data allow us to characterize the universe of trip sponsors as dominated by a few recurring actors but populated with many sponsors total. Our analysis opens a new avenue for research on the interaction between members of Congress and interest groups.}

\newpage

At the end of May 2013, ten members of Congress, along with thirty-two staffers and dozens of state legislators, traveled to the Baku, Azerbaijan. Gathering on the shore of the Caspian Sea, they took part in an all-expense-paid conference and cultural visit. The members and their staff listened to speeches given by the president of Azerbaijan, three former advisors to President Obama, and attended at least three briefings pertaining to the country's state-owned oil company. The representatives, many of whom brought along their spouses, also partook in local festivities, such as a fireworks show for the Republic Day of Azerbaijan, and a tour of the Old City.

The trip sparked controversy when it was reported that the Azerbaijan-affiliated nonprofits that sponsored the travel had used money originating from a state agent, the very same state-owned oil company that had held information sessions during the conference [@Tucker2014]. While it is legal for nongovernmental organziations to pay for members to go on such excursions, it is forbidden for members to accept travel offers from foreign countries or corporations that employ U.S. lobbyists, as well as meet with lobbyists at any time during their travel [@Wickham2015]. As per House rules, the members had all received approval from the House Ethics Committee before going to Baku, but, upon returning to the United States, they failed to report the foreign and corporate sponsorship [@Tucker2014].

The *Washington Post* speculated that the trip, and the courtship of which it was a part, may have played a role in a few of members' decisions to sponsor amendments that exempted an Azerbaijani pipeline project from a sanctions bill that was under consideration at the time [@Choma2015; @Higham2015]. The Office of Congressional Ethics ultimately recommended to the House Ethics Committee that the investigation into nine members who violated House code and federal law be further reviewed, and it was handed off to the Department of Justice [@OCE2015]. The Baku trip is known as *gift travel* in Capitol parlance, and this episode in particular highlights the potential for gift travel to be gamed by the sponsors, the laxness of the self-reporting system, and the difficulty in connecting what goes on during these trips with legislators' preferences and behavior. While this particular trip was unusual because it broke House rules, and maybe federal law (e.g., the Emoluments Clause), in many other ways it was an ordinary instance of gift travel. Members were invited by a nonprofit to listen to speeches in and tour around a foreign country. The speeches, briefings, and mingling were all a part of what a member typically experiences on a gift-travel trip. To be more explicit, gift travel occurs when a member, or one of her staff, goes on an expense-paid trip sponsored by a non-governmental organization, such as a trade association, think tank, cable channel, or university. When members go on these sponsored trips, they must report it to the Clerk of the House[^1].

Gift travel is an important, but understudied, example of representative behavior. Members receive campaign contributions from dozens of PACs and private individuals, but they are on average going on five trips provided by five sources each Congress. Going on an expense-paid trip, versus accepting donations, is more meaningful for a relationship between a member and an interest group because that member chooses to spend valuable time to participate. It is much more active than simply receiving a check. Therefore, with the Baku scandal in mind, we argue that interest groups provide members with gift travel as an attempt to buy access and influence their policy preferences.

Learning about gift travel behavior informs us about how members spend their time and resources on an unseen realm of information exchange sponsored by groups seeking influence in the policy process. Unfortunately, we still lack answers to basic questions such as "how much gift travel do members go on" and "what organizations are the most popular sponsors?" This paper provides a first look at this specific kind of travel behavior while also attempting to understand the dynamics between these members and the interest groups sponsoring their trips.

[^1]: According to Rule XXV, clause 5 of the Rules of the House of Representatives, members must disclose reimbursement for such travel within 15 days of return [@Wickham2015]. The Clerk of the House makes a report of these disclosures public on its website. Rule XXV is also clear that no such gift travel can be paid for by a registered lobbyist or by the agent of a foreign principal, and neither can a registered lobbyist or agent of a foreign principal be present at any time during the trip. There are a few exceptions where members of Congress may have their travel paid for by foreign governments. These exceptions are usually when foreign governments pay for in-country expenses or travel for members visiting the sponsoring country. There are limitations for how long these foreign-government-paid trips may be, and oftentimes these trips must be pre-approved by the relevant committee.

We theorize that sponsoring organizations seek short-term policy influence, information exchange, and the opportunity to have the member's attention. Therefore we conjecture that groups target members who are strategically positioned to influence policy. We expect high-ranking, electorally safe, and senior members to travel more, and ideologically extreme members to travel less. We have three major findings. First, party leaders, committee chairs, and ranking members travel much more than the rank and file. Second, seniority is not a significant predictor of the number of gift travel trips a member goes on, and electoral safety has a trivial effect. Third, and unexpectedly, greater ideological extremeness is associated with more gift travel rather than less. We will now proceed by exploring what we know about the relationship between interest groups and Congress as well as what we know about the travel of members. Following that we will discuss our hypotheses, data, and findings. We close the paper with a discussion of our findings' implications and suggestions for avenues of future research on gift travel.

# Interest Groups and CODELs

Clearly, members of Congress and interest groups have a dynamic relationship. They are engaged in a mutually beneficial give-and-take and the American public is regularly suspicious about the potential for corruption between these groups and their representatives. Suspicious of these relationships too, political scientists have investigated how interest groups, corporations, and think tanks---and their respective PACs---attempt to influence policymakers. The empirical evidence with regard to exogenous actors directly "buying" members votes has not found much of a relationship [@Welch1982; @Wright1990]. However, contributions that are timed correctly, such as before critical votes, have given scholars pause [@Stratmann1998]. And, certain groups seem to invest in members long-term [@Snyder1992].

A more nuanced type of influence is more likely. Hall and Wayman [-@Hall1990] argue that contributions lead to less measurable changes, like shifts in the content of bills. It is also possible that interest groups provide critical information or services that make the lives of already overwhelmed legislators easier [@Hall2006]. Langbein [-@Langbein1986] argues that money buys access to members of Congress and estimates that a PAC would need to contribute approximately $72,000 for one hour with a member. A more nuanced type of influence is likely at work with gift travel as well.

The study of when and where members of Congress travel is not new. For instance, scholars have investigated where, how often, for how long, and with whom, members travel abroad as part of Congressional Delegations, or CODELs in D.C. argot [see for example @Alduncin2014; @Alduncin2017]. Some CODELs are partisan, others are bipartisan, but they are usually conducted in groups, presumably for the purpose of learning something valuable to their jobs as legislators.[^2] Alduncin et al. [-@Alduncin2014] find that trips abroad are getting shorter and, in general, members are spending less time together. With members spending less time together, the authors argue that the social fabric within the institution is fraying. Alduncin, Parker, and Theriault [-@Alduncin2017, 1] find a still fraying social fabric and argue that bipartisan foreign travel has become "a victim of the partisan war waging in Congress." Their conclusion was drawn from the bleak realities of their findings, which were that (among other things) extremely conservative House Republicans have become much more likely to travel with only co-partisans. The effects are similar, but of a lesser magnitude for moderate Republicans.

[^2]: CODELs differ from gift travel in important ways. For general CODEL trips abroad, when members want to travel they must first request permission and funding from the parent chamber or relevant committee. Gift travel, however, requires a sponsoring organization and therefore is much more susceptible--theoretically--to quid pro quo corruption. Another important difference is that members in CODELs can ask fellow members if they would like to participate in a delegation trip. Again, gift travel differs in that the sponsoring organization selects who travels. With the power to target individual members in the hands of the sponsors, it is important to understand this potential mechanism of influence.

We will rely on the literature on foreign travel among members of Congress to inform our hypotheses about gift travel, since foreign travel is the nearest thing to gift travel that scholars have studied. The key difference to keep in mind is that delegation and committee travel are the product of members' initiative while gift travel starts, at least in theory, with the sponsor

# The Causes of Gift Travel

Gifts imply relationships. Every gift-giving situation involves a giver and a recipient. Gifts are usually given as an expression of love, respect, or appreciation, and while they are not given with the expectation of reimbursement, they can be given with the expectation of reciprocity [@Graeber2011]. The relevant question here is: Which members are most likely to reciprocate a sponsor's gift? Reciprocation in this situation would mean that the member had improved the chances that the sponsor's policy preferences became law. Gift travel is not a direct campaign contribution, and therefore it may be perceived as a less "direct" source of influence. But, since gift travel is a relatively hidden activity (from the public's perspective), it may be a powerful avenue of influence for sponsors of travel.

We posit that sponsors are organizations that are looking for short-term influence on policymaking, and sending members to conferences and on fact-finding missions is an attempt to "educate" them, and be "educated" in return, in light of that purpose. Sponsors are strategic actors and will not waste their gift resources on members who cannot or will not improve their chances of influencing policymaking.

*Power hypothesis* Members who have more power, such as party leaders and committee chairs, are the first place to look for targets of gift travel. As powerful members, it would make sense for them, ceteris paribus, to receive more invitations and to go on more gift journeys than less powerful members. Influencing members in leadership positions means influencing the legislative agenda, especially in the form of negative agenda control wherein leaders can tilt policymaking in favor of the status quo [@Cox2005].

*Seniority hypothesis* As Alduncin, Parker, and Theriault [-@Alduncin2017] point out, senior members may also be more likely to shift their attention toward legislation and policymaking, so there may be some causation going in the other direction; that is, senior members may cultivate relationships with travel-gifting interest groups because they want to learn about policy, or they want information gains from those interest groups [@Hall2006].

*Safety hypothesis* Members with large margins of victory, because they are often from ideologically aligned districts, are more likely to pursue national-level policy issues [@Grimmer2013a]. Therefore, we should also expect that electorally safer members have more latitude to build relationships with travel-gifting groups. These safer members should then take more trips at these groups' expense.

*Ideology hypothesis* As for the direct effect of members' political ideology, there is an interesting difference in how ideology may come into play in foreign travel as opposed to gift travel. @Alduncin2017 speculate that more ideologically extreme members would tend to travel abroad less because they would be less inclined to think that they had something to learn from how foreign countries do things. They report that conservative Republicans have always been less likely to travel. The authors further speculate that, because foreign travel often entails flying with members of the other party, ideologically extreme members will travel less than more moderate members.

The first speculation applies partially to gift travel because some sponsored trips are to foreign countries for the purpose of learning about social and political life abroad; other trips, however, keep members in the United States and can bring them to ideologically charged events, such as those held by think tanks like the Heritage Foundation. Therefore, because gift travel may be more conducive to ideology-affirming experiences than foreign travel, ideological members may be no different than moderate members in their quantity of travel.

Whether or not ideological members are advantaged over moderate members depends on the sponsor organizations and their motives. If sponsors as a group are highly ideological, and they seek out likeminded legislators in order to give them information subsidies [@Hall2006], then more ideological members should travel more. Our hypothesis will remain what previous literature has found, but with the thought in mind that the sponsor-led nature of gift travel may result in different patterns than foreign travel.

The second speculation is less obviously relevant than the first to gift travel because gift travel need not be conducted as part of a group, and sponsors decide the composition of the group if there is one. Bipartisan gift travel is not unheard of, however. There are instances, such as the entire Indiana delegation going on a trip sponsored by a soybean farmers' trade association, where members of different parties travel together. State-delegation excursions appear to be the exception rather than the rule though. Notably, we find that sponsors seem to hand-select which members they send on trips.

# Data

The data for this analysis come from the Office of the Clerk of the U.S. House of Representatives. Every year since 2007, the Clerk has published all gift travel reports [@Dent2015, 11]. This paper analyzes these reports from the 110th through the 114th Congresses (2007-2017). These data, after cleaning, collapsing duplicate trip entries, and aggregating by member, consist of 2180 observations, which are at the level of the member per Congress. Over the course of the ten-year period for which we have data, members reported spending 42,388 days engaged in gift travel, with each member traveling an average 19 days per biennium.[^3]

[^3]: Note that although every trip is reported in connection with a member, members themselves do not go on all trips; sometimes staffers are sent in their stead.

### Sponsors; or, the Givers

It is worth pausing to observe some basic facts about the organizations behind all this gift travel: the sponsors. A glance at the list of reports quickly shows that there is not a standard or system by which members are filling out their gift-travel paperwork. The Clerk's dataset does not provide a simple answer to the question of how many unique organizations are taking advantage of gift travel because filing is left up to the members and their staffs. It it up to them to spell the name of the sponsor correctly, use the full name or an abbreviation, and, indeed, know exactly who it is that is sponsoring the trip. After attempting to correct for typos and various names for the same organization, we found that a total of 1466 nongovernmental sources provided reimbursement for travel to members of Congress between 2007 and 2017. The true number is doubtless smaller, but it seems safe to say that at least 1000 different organizations gave at least one gift-trip in that ten-year period, which equates to about 250 organizations per Congress, with each cohort experiencing about 2500 trips.

We also might wonder whether travel sponsors are an egalitarian bunch, each giving roughly the same number of trips per Congress, or whether the travel-sponsor universe is characterized more by a few heavy hitters that account for the bulk of members' gift travel year after year. As it turns out, a small number of familiar names are responsible for a hefty portion of the number of trips taken each Congress. Only about 4% (63 out of 1466) of the sponsoring organizations averaged at least one trip per Congress, or five total in the data set. This datum would imply that only five or six dozen organizations are taking the cost of putting members on trips as a regular part of business. The other 95% or so appear to be using gift travel only sparingly, perhaps in relation to special opportunities or changes in the policy information environment [@Jones2005].

The sixty-two organizations that on average sponsored one or more trips per Congress account for 72% of the all the reported trips in our data set. That is, roughly three out of every four trips are sponsored by the same sixty-three groups. The concentration of gifting behavior among a handful of sponsors is an important descriptive fact to note. Our theoretical expectation is that more powerful members will travel more often, and if the same sponsors are doing so over and over, then this makes it likely that travel sponsors are generally well-funded and strategic, not circumstantial or one-off givers.

To get some notion of who the big players are, let's look briefly at the top five sponsors. The most active sponsor, by far, is an organization called the Congressional Institute, which provided travel subsidies an average of 370.8 occasions per Congress. Judging from the reports, the Congressional Institute seems to invite great numbers of members, usually around 150 of them, to places near Washington, such as Hot Springs, VA. The Institute claims to advocate for congressional reform; for example, promoting the idea of a joint committee that will propose changes to rules and procedures followed in the House and Senate. The remaining groups are the American Israel Education Foundation (146.0 trips per Congress), the Aspen Institute (107.4), the Heritage Foundation (88.4), and the Humpty Dumpty Institute (45.6) round out the top five. The Aspen Institute and the Heritage Foundation are think tanks; the Humpty Dumpty Institute is an international NGO; and the American Israel Education Foundation is an interest group, self-described as being part of America's pro-Israel lobby. Each of these organizations clearly has a policy solution to offer or a policy problem it hopes to push onto the congressional agenda.

### Dependent variable

We have one primary dependent variable: *trips*. It is a count, i.e., a sum of binary items (traveled or did not), and it is over-dispersed.[^4] Further, there is heterogeneity across individuals' probabilities of traveling. Each member of Congress does not have an equal probability of being selected to travel by a sponsoring organization. This is especially true of party leaders or committee chairs where some members hold more power or policy expertise than rank-and-file members. Therefore, we estimate a negative binomial regression using maximum likelihood. We include fixed-effects for each Congress.

[^4]: Overdispersion occurs when the observed variance is larger than the expected variance from a given model [@Collett2003]. The count is the number of separate journeys reported by each member to the Clerk of the House; each unique report counts as one trip.

Not all members go on gift travel, but most of them do. Of the 2180 total members, 292 (13.4%) did not go on a single trip. Similarly, 253 members (11.6%) went on exactly one, 42 (11.4%) went on two, 255 (11.7%) went on three, with 4.8 trips being the mean. Figure 1 shows a histogram of the number of trips taken by all the members. The figure is heavily right-skewed (mean = 4.8, sd = 4.7, median = 4), with only 30 members going on 20 or more trips. The member to go on the most trips, 50, was Fred Upton (MI-R), both a committee chairman and a senior member. Louise Slaughter (NY-D), another senior member in a high-ranking committee position, though in the minority party, went on zero trips during the 114th Congress.

```{r, echo = F, message = F, fig.cap = "Histogram of Trips (2007-2017)"}
library(ggplot2)
library(MASS)
giftdata <- read.csv(file = "110-114Congresses.csv", header = TRUE, stringsAsFactors = FALSE)
ggplot(data = giftdata, aes(x=trips)) + geom_histogram(color="black", fill="purple", alpha=0.4) + theme_classic() + labs(x="Number of Trips", y="Number of Members")
```

Democrats travel less often, on average, compared to Republicans (see Figure 2). The average number of trips among Democrats is 4.3, but the variance is large ($\sigma^2 = 23.7$). Republicans, on average, go on one more trip than Democrats; their average is 5.2, but again, the variance is large ($\sigma^2 = 20.3$).

```{r, echo = F, message = F, fig.cap = "Histogram of Trips (2007-2017) by Party"}
library(ggplot2)
library(RColorBrewer)
giftdata <- read.csv(file = "110-114Congresses.csv", header = TRUE, stringsAsFactors = FALSE)
ggplot(data = giftdata, aes(x = trips, fill = as.factor(party))) + geom_histogram(alpha=0.8, position="stack") + theme_classic() + scale_fill_manual(name =c("Legend"), values=c("blue", "red"), labels=c("100"="Democrats", "200"="Republicans")) + labs(x="Number of Trips", y="Number of Members")
```

### Explanatory variables

The win percentage data were provided by Sean Theriault; the seniority, committee membership, and leadership data were gathered independently. We adjusted the win percentage observations for those members in California who ran against copartisans in the general election because of California's unique primary system. Instead of being given 100% of the vote share, Democrats who defeated other Democrats, for example, were tallied as having won with whatever percentage they got in the general election. This adjustment corrects for what may have been an overestimate of the number of unopposed members.

Party and ideology (roll-call summary) data were downloaded from the voteview.org website now under the auspices of Jeff Lewis. To create our measure of *ideological extremity*, we start with the Common Space DW-NOMINATE scores, and then calculate the distance, in absolute value, of each member from the opposing party's mean. Leadership is operationalized in three different ways. We code for *committee chairs*, *ranking members* and *party leaders*, where party leaders are the Speaker, the majority or minority leader, a whip, or the chair of either the Republican or Democratic caucus.

# Models and Results

## Results

Do members of Congress differ in how many gift trips they go on? What characteristics separate those who travel often from those who stay in Washington or travel only home to their districts? The results from our statistical analysis offers answers to these questions. As our theory led us to expect, members in positions of power---party leaders, committee chairs and ranking members---on average go on significantly more gift trips than the rank and file. The statistically significant parameter estimates for the power variables indicate that powerful members travel more, but they do not give us a clear idea of how many more trips per Congress they go on. For the substantive meaning of the estimates, we calculate the contribution each explanatory variable makes to the predicted number of trips, and we plot the changes in Figure X. For instance, holding all other power variables at zero and the continuous variables, *seniority*, *win percentage*, and *ideological extremity*, at their sample means, the effect of being party leader is sizable: a party leader is predicted to go on 5.49 trips per Congress, three more trips than a rank-and-file member, an increase of 113%.

Members in the highest positions of their committees also travel at a higher rate. For members of both parties, the effect of being a committee chair is almost identical in size to being a party leader, while the effect of ranking member differs across party. Republican ranking members do see a significantly larger amount of travel, going on an estimated 2.25 more trips (87% increase). The same is not true for Democratic ranking members in our data. Though larger, the number of trips they go on is not statistically different from the number of trips non-ranking members take. Why this should be so is unclear.

The interactive effect of ideological extremity and party on the number of gift-travel trips members go on is the second major finding of this paper. It is important not only because the magnitude of its effect is large but also because it reveals how ideology works to attract sponsors toward members in different degrees depending on their party. The first thing to note is that ideologically extreme members are more likely than their moderate colleagues to venture out at the invitation of sponsoring organizations. The large positive effect of ideological extremity holds for members of both parties. But the size of the effect is larger for Democrats than it is for Republicans. The estimated number of trips for Republicans rises from 2.1 to 3.3 (57% increase), while the number for Democrats jumps from 0.9 to 4.8 (433% increase). So, what a Democrat may lack in committee power in the eyes of sponsors, she may make up for in ideological constancy.

We also find some interesting null effects. Though we expected otherwise, more senior and electorally safe members are no more likely than their marginal freshman counterparts to take a trip on someone else's dime. The fixed effects for Congressional term provide us with further information, namely that gift travel appears to be steadily increasing in frequency since records began in 2007. Gift travel is an increasingly popular activity. Lastly, it is important to note that, all things considered, Republicans of the rank and file go on average 2.6 total trips per Congress, which is 0.4 trips (18%) more than similar Democrats. Republicans in general have been going on more gift travel than Democrats.  

--- R Results
<!---
Our full model includes members from both parties $(n=2180)$, which we account for by including a variable that indicates whether a member is a Democrat or not. From the negative coefficient on our party variable we can confirm what we saw from our descriptive statistics---Democrats travel less frequently than Republicans. The remaining independent variables have positive and significant coefficients. Safer members tend to travel more, but only slightly. More ideologically extreme members travel more, contrary to our theoretical expectations. Ideological extremity has the largest effect among our explanatory variables. Before speculating too much on our ideology finding, we will see if extremity has the same effects among Democrats and Republicans. Gift travel may be an avenue for ideological groups to reward loyal members and provide them with information subsidies.
--->


\begin{table}[]
\centering
\caption{Predicted Number of Trips}
\label{}
\begin{tabular}{@{}lll@{}}
\toprule
                            & 0                 & 1                 \\ \midrule
Committee Chair             & 2.58              & 5.52              \\
                            & {[}2.33 - 2.85{]} & {[}4.62 - 6.59{]} \\
Democrat                    & 2.58              & 2.17              \\
                            & {[}2.33 - 2.85{]} & {[}1.97 - 2.39{]} \\
Party Leader                & 2.58              & 5.49              \\
                            & {[}2.33 - 2.85{]} & {[}4.20 - 7.17{]} \\
Ranking Member (Democrat=0) & 2.58              & 4.83              \\
                            & {[}2.33 - 2.85{]} & {[}3.75 - 6.22{]} \\
Ranking Member (Democrat=1) & 2.17              & 2.49              \\
                            & {[}1.97 - 2.39{]} & {[}1.98 - 3.15{]} \\ \bottomrule
\multicolumn{2}{l}{\footnotesize Note: Standard errors in parentheses}    \\
\end{tabular}
\end{table}

```{r, echo = F, warning = F, message = F, fig.cap = "Predicted Trips Taken per Congress"}
library(ggplot2)
library(dplyr)
library(RColorBrewer)
#set up data and multiplot function
giftdata <- read.csv(file = "110-114Congresses.csv", header = TRUE, stringsAsFactors = FALSE)
finalmodel <- glm.nb(trips ~ extreme*democrat + winpct + committee*democrat + seniority + chairman + party.leader + fourteenth + thirteenth + twelfth + eleventh, data = giftdata)
multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
  library(grid)

  # Make a list from the ... arguments and plotlist
  plots <- c(list(...), plotlist)

  numPlots = length(plots)

  # If layout is NULL, then use 'cols' to determine layout
  if (is.null(layout)) {
    # Make the panel
    # ncol: Number of columns of plots
    # nrow: Number of rows needed, calculated from # of cols
    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                    ncol = cols, nrow = ceiling(numPlots/cols))
  }

 if (numPlots==1) {
    print(plots[[1]])

  } else {
    # Set up the page
    grid.newpage()
    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))

    # Make each plot, in the correct location
    for (i in 1:numPlots) {
      # Get the i,j matrix positions of the regions that contain this subplot
      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))

      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                      layout.pos.col = matchidx$col))
    }
  }
}

#predicted values
extremitydata <- data.frame(extreme = giftdata$extreme, democrat = 0, winpct = mean(giftdata$winpct), seniority = mean(giftdata$seniority), chairman = 0, committee = 0, party.leader = 0, fourteenth = 0, thirteenth = 0, twelfth = 0, eleventh = 0)
extremitydataD1 <- data.frame(extreme = giftdata$extreme, democrat = giftdata$democrat, winpct = mean(giftdata$winpct), seniority = mean(giftdata$seniority), chairman = 0, committee = 0, party.leader = 0, fourteenth = 0, thirteenth = 0, twelfth = 0, eleventh = 0)
extremitydataD1 <- filter(extremitydataD1, democrat == 1)
winpctdata <- data.frame(extreme = mean(giftdata$extreme), democrat = 0, winpct = giftdata$winpct, seniority = mean(giftdata$seniority), chairman = 0, committee = 0, party.leader = 0, fourteenth = 0, thirteenth = 0, twelfth = 0, eleventh = 0)
senioritydata <- data.frame(extreme = mean(giftdata$extreme), democrat = 0, winpct = mean(giftdata$winpct), seniority = giftdata$seniority, chairman = 0, committee = 0, party.leader = 0, fourteenth = 0, thirteenth = 0, twelfth = 0, eleventh = 0)
extremitydata$phat <- predict(finalmodel, extremitydata, type = "response")
extremitydataD1$phat <- predict(finalmodel, extremitydataD1, type = "response")
winpctdata$phat <- predict(finalmodel, winpctdata, type = "response")
senioritydata$phat <- predict(finalmodel, senioritydata, type = "response")

#prep for plots
extremitydataCI <- data.frame(extremitydata)
extremitydataCI <- cbind(extremitydataCI, predict(finalmodel, extremitydata, type = "link", se.fit = T))
extremitydataCI <- within(extremitydataCI, {
  Trips <- exp(fit)
  LL <- exp(fit - 1.96 * se.fit)
  UL <- exp(fit + 1.96 * se.fit)})

extremitydataD1CI <- data.frame(extremitydataD1)
extremitydataD1CI <- cbind(extremitydataD1CI, predict(finalmodel, extremitydataD1, type = "link", se.fit = T))
extremitydataD1CI <- within(extremitydataD1CI, {
  Trips <- exp(fit)
  LL <- exp(fit - 1.96 * se.fit)
  UL <- exp(fit + 1.96 * se.fit)})

winpctdataCI <- data.frame(winpctdata)
winpctdataCI <- cbind(winpctdataCI, predict(finalmodel, winpctdata, type = "link", se.fit = T))
winpctdataCI <- within(winpctdataCI, {
  Trips <- exp(fit)
  LL <- exp(fit - 1.96 * se.fit)
  UL <- exp(fit + 1.96 * se.fit)})

senioritydataCI <- data.frame(senioritydata)
senioritydataCI <- cbind(senioritydataCI, predict(finalmodel, senioritydata, type = "link", se.fit = T))
senioritydataCI <- within(senioritydataCI, {
  Trips <- exp(fit)
  LL <- exp(fit - 1.96 * se.fit)
  UL <- exp(fit + 1.96 * se.fit)})

#plots
mypalette <- brewer.pal(3,"Purples")
p1 <- ggplot(extremitydataCI, aes(extreme, Trips)) +
  geom_ribbon(aes(ymin = LL, ymax = UL, fill = democrat), alpha = .25) +
  geom_line(aes(colour = committee), size = 1) +
  labs(x = "Ideological Extremity", y = "Predicted Trips-Republicans") + guides(colour=FALSE, fill=FALSE) + scale_fill_distiller(palette = mypalette, type = "seq") + scale_color_distiller(palette = mypalette, type = "seq") + theme_classic()
p2 <- ggplot(extremitydataD1CI, aes(extreme, Trips)) +
  geom_ribbon(aes(ymin = LL, ymax = UL, fill = chairman), alpha = .25) +
  geom_line(aes(colour = party.leader), size = 1) +
  labs(x = "Ideological Extremity", y = "Predicted Trips-Democrats") + guides(colour=FALSE, fill=FALSE) + scale_fill_distiller(palette = mypalette, type = "seq") + scale_color_distiller(palette = mypalette, type = "seq") + theme_classic()
p3 <- ggplot(winpctdataCI, aes(winpct, Trips)) +
  geom_ribbon(aes(ymin = LL, ymax = UL, fill = committee), alpha = .25) +
  geom_line(aes(colour = committee), size = 1) +
  labs(x = "Win Percentage", y = "Predicted Trips") + guides(colour=FALSE, fill=FALSE) + scale_fill_distiller(palette = mypalette, type = "seq") + scale_color_distiller(palette = mypalette, type = "seq") + theme_classic()
p4 <- ggplot(senioritydataCI, aes(seniority, Trips)) +
  geom_ribbon(aes(ymin = LL, ymax = UL, fill = fourteenth), alpha = .25) +
  geom_line(aes(colour = fourteenth), size = 1) +
  labs(x = "Terms Served in the House", y = "Predicted Trips") + guides(colour=FALSE, fill=FALSE) + scale_fill_distiller(palette = mypalette, type = "seq") + scale_color_distiller(palette = mypalette, type = "seq") + theme_classic()

multiplot(p1, p3, p2, p4, cols=2)
```

# Discussion

We have modeled the gift-travel behavior of members of Congress as a function of their party, their time spent in office, the safeness of their seat, their role as either leader or rank and file, committee rank, and ideological extremity (or the degree to which they vote with their party and not with the other). Prior research on members' travel behavior, though not gift travel, led us to expect that electoral safety and seniority would be associated with a greater willingness of members to venture out of the capital, but we do not find evidence of this. Instead we find strong evidence in favor of the power hypothesis, which suggests that sponsoring organizations target members with agenda-setting power for travel opportunities.

Members who are party leaders or who fill powerful positions in their respective committees are far more likely to go on gift travel than their colleagues. It makes sense for sponsors to want to influence these powerful members. Party leaders and committee chairs control the legislative calendar, write the rules for debate on the floor, and decide who testifies on bills; in other words, they have significant agenda influence [@Cox2005]. Party leaders and committee chairs also maintain a near-monopoly on the flow of information within the chamber, often restricting the legislative influence of rank-and-file members on crafting legislation [@Curry2015]. As the legislative process continues to centralize in the House, we should expect to see this targeting of party leaders and committee chairs by sponsors to continue. Rank-and-file members do, however, go on their fair share of trips. Rank-and-file influence on the legislative process is present, it is just oftentime more nuanced. For example, consider when subsets of members--especially caucuses or ideological factions--band together to influence the legislative process [@Rohde1991;@Hammond2001;@Rubin2017]. And, lest we forget, rank-and-file members do retain negative agenda control too [@Cox2005]. Therefore, we were not surprised to see sponsors invest in the rank-and-file and we expect them to continue to do so in the future--but still at rates lower than powerful members.

In the aim of parsimony, we have estimated but a single model for both parties while measuring the effect of party and including interaction terms for the relationships that held up statistical significance. The most important of these was the interactive effect of party on ideological extremity. Our results were surprising in two ways. First, far from being a damper on travel, ideological extremity was found to be a catalyst for more trip-taking. Second, its catalyzing effect was sharply pronounced for Democratic members, the most ideologically extreme of whom were estimated to travel over 400% more per Congress than the most moderate. Why this should be so is not immediately obvious. The logic of rank-and-file members retaining influence by banding together provides some support here. If a group of rank-and-file members appears to be able to influence the legislative process they would certainly attract more support from interest groups seeking to educate members for their policy causes. Or, perhaps the explanation is much simpler. It is possible that sponsors are themselves ideologically motivated and they are merely seeking a forum for likeminded ideological members to discuss new policy solutions or policy problems. Better understanding this relationship between increases in gift travel and ideological extremity represents a rich area for future research.

<!---
With all of our data on the table, let's consider how our hypotheses fared. In all three models, the power hypothesis variables did a large proportion of the explanatory work. In each model, being a party leader or committee chair led to significantly more trips than the average member. The only caveat we found was that Democratic ranking members did not have statistically significant increases in trips. Our safety hypothesis, that electorally safe members would be more attractive bets for sponsoring organizations, turned out to be correct across the full model and the Democratic model, but the effect-size was minuscule in both cases. Seniority was statistically significant in our full model and did increase the number of gifted trips. But, seniority defied our expectations and appeared insignificant in the party-specific models. There is a very weak relationship between time served and number of gifted trips taken by members. We interpret this to mean that sponsoring organizations are most interested in targeting members with the power to impact legislation in the most meaningful ways. As the legislative process continues to centralize in the House, we can expect to see this targeting of party leaders and committee chairs by sponsors of gift travel continue.

Our ideology hypothesis, that ideologically extreme members will travel less, turned out to be wrong. While ideological extremity was significant across all three models, the direction was the opposite of what we theorized. We found that ideological extremity leads to more gift travel. In fact, in the Democratic model, ideological extremity had the largest effect of all the variables. This is not entirely surprising; some scholars argue that interest groups are aligned with one party or the other and that such alignment is driven by policy interests [@Koger2010]. If these policy and party interests align, gift travel might be the perfect avenue for influence by an interest group. Future work should investigate whether ideological similarity, as opposed to extremity, is the driving force here, as it may turn out that sponsoring organizations are themselves skewed toward the ideological poles.

The last set of findings we present addresses the role of a member's party controlling the chamber. We found that majority status increases Republican members' number of trips, but decreases Democratic members' number of trips. Overall, we think this measure of majority status is actually picking up on district- or constituency-specific effects in a crude way. We do not currently have the data to model such explanatory factors, but this is a fertile area for future gift-travel research.

We don't know wehre members are going well; we don't know if where Ds go and Rs go differs; we don't know if Ds or Rs are going abroad more and what that means. Are leaders going on different sorts of trips than rank and file?
--->

# Conclusion

Are interest groups sponsoring members travel to influence their preferences? While the evidence we present is not sufficient for a full-throated 'yes,' it may be sufficient to say 'probably, so let's keep searching.' The specific targeting of powerful members (i.e. party leaders, committee chairs, and ranking members) indicates, at minimum, that more research needs to be done on the mechanism of gift travel. If possible, an explication of what types of groups sponsor any gift travel at all and a closer look at activity within the U.S. House following trips would better shed light on the question of quid pro quo corruption from these excursions.

Furthermore, a proper continuation of scholarship regarding the travel of members [@Alduncin2014; @Alduncin2017] would examine who travels with whom and how often. Using what the Clerk of the House provides, future research could work to determine which members were visiting the same locations at the same times, and use this information to investigate how member-level attributes relate to the partisan nature of their gift-travel behavior. Many trips gifted during the Congresses analyzed here involved members traveling together, and we still have yet to find out if party polarization's effect on CODEL travel is felt also on gift travel.

Future scholarship on member travel should also try to better specify the relationship between sponsors and members. A measure of sponsor ideological similarity would go a good ways in specifying the relationship, as would a more nuanced coding of the committee-related variables. Like sophisticated donors, sponsors may also target the committees most relevant to their policy goals [@Barber2017]. Or, perhaps sponsors target ideologically similar members for travel [@Barber2017]. Our analysis speaks to who travels and how much, but future work should investigate whether those who travel more do so because they receive trips from a wide variety of sponsors or because they are given trips again and again by the same big organizations.

One final note is that all trips are not the same, and what we have modeled here is a mere count of the quantity of trips taken by members of Congress. Some trips are domestic, others are overseas; some trips are a day long, others are a week long; some are taken alone, others are in experienced groups. The varieties of trip offer us several more questions we could ask about what these excursions mean. 

Gift travel is an overlooked aspect of members' relationships with interest groups and non-governmental organizations. Many questions remain unanswered. How does gift travel change over extended periods of time? What is it good for? How effective is it as a mechanism for interest groups? Researchers should appreciate the potentially important things we have to learn from this unusual form of documented lobbying and travel and we hope to work toward answering these questions in the near future.

# Appendix

For those interested in the new dataset utilized in this paper, we have prepared a few descriptive statistics for transparency. After grouping all trips according to the members who went on those trips, we are left with a dataset comprised of 2180 members. There are a few extra members than may be expected because some members were replaced during the course of the Congress. Let's turn to some description of the members themselves. The average number of terms, our measure of seniority, is 5.7, sd = 4.6. In other words, the average member is in about their sixth term of service. The average win percentage was about 68% with a standard deviation of 13 percentage points. A full 165 (7.5%) of the members were unopposed in their election; they won with 100% of the vote. Our dataset represent periods of both full Democratic and full Republican majorities in Congress. And, the final Congress in our dataset (the 114th) was the largest majority the Republicans had controlled of the House since 1929 (Bump 2014). Additional information is available upon request.

# References
