---
title: "Gift Travel in the U.S. Congress"
author: "Philip R. Moniz & Zachary A. McGee"
date: "7/3/2017"
output: pdf_document
bibliography: /Users/philipmoniz/Documents/Scholastic Scribblings/my_library.bib
#bibliography: /Users/zacharymcgee/Dropbox/Library/library.bib
casl: /Users/philipmoniz/Documents/Scholastic Scribblings/apsa.csl
---

When members of Congress travel abroad on official business, as part of what are called Congressional Delegations, CODELs in Capitol parlance, they must report this travel to the Clerk of the House. Scholars have investigated where, how often, for how long, and with whom, members travel abroad (see for example [@Alduncin2014; @Alduncin2017]). When they want to travel as part of a Congressional Delegation, members must first request permission and funding from the parent chamber or relevant committee. Members can also be asked by other members if they would like to participate in a delegation trip. Some CODELs are partisan, others are bipartisan, but they are usually conducted in groups, presumably for the purpose of learning something valuable to their jobs as legislators, though some members have been criticized by challengers for wasting taxpayer money on pleasure trips.

While members can apply for travel paid for by the federal government, there is another way that members can get out of the house: gift travel. Gift travel comprises journeys that are paid for by a non-governmental source, and these trips can be within or without the United States. According to Rule XXV, clause 5 of the Rules of the House of Representatives, members must disclose reimbursement for such travel within 15 days of return [@Wickham2015]. The Clerk of the House makes a report of these disclosures public on its website. Rule XXV is also clear that no such gift travel can be paid for by a registered lobbyist or by the agent of a foreign principal, and neither can a registered lobbyist or agent of a foreign principal be present at any time during the trip.[^1]

[^1]: There are a few exceptions where members of Congress may have their travel paid for by foreign governments. These exceptions are usually when foreign governments pay for in-country expenses or travel for members visiting the sponsoring country. There are limitations for how long these foreign-government-paid trips may be, and oftentimes these trips must be pre-approved by the relevant committee.

Gift travel must also be for the purpose of official business. Members are not supposed to accept reimbursement for trips conducted primarily for leisure or diversion; such trips, of course, would give the appearance of corruption. Gift travel allows non-governmental organizations, such as trade associations, non-profits, think tanks, and universities to invite members of Congress to conferences, conventions, dinners, and other types of events. But why do non-governmental organizations choose to fly members to their events? Are some members more likely to be invited than others, and if so, why?

Answers to basic questions such as "how much gift travel do members go on?" and "what organizations are the most popular sponsors" are unanswered in the literature on members' travel behavior. This paper will provide a first look at this specific kind of travel behavior. We will rely on the literature on foreign travel among members of Congress to inform hypotheses about gift travel since foreign travel is the nearest thing to gift travel that scholars have studied. The key difference to keep in mind, however, is that delegation and committee travel are the product of members' initiative while gift travel starts, at least in theory, with the giver.

# The Causes of Gift Travel

Gifts imply relationships. In any gift-giving situation, there is a giver and a recipient. Gifts are usually given as an expression of love, respect, or appreciation, and while they are not given with the expectation of reimbursement, they can be given with the expectation of reciprocity [@Graeber2011]. The relevant question here is: "Which members are most likely to reciprocate a sponsor's gift?" Reciprocation in this situation would mean that the member had improved the chances that the sponsor's policy preferences became law. Money can be seen as the clearest type of gift to members; yet, scholars have found little evidence of direct campaign contributions impacting roll-call votes [@Welch1982; @Wright1990]. Gift travel is not a direct campaign contribution, and therefore it may be perceived as a less "direct" source of influence. But, since gift travel is a relatively hidden activity (from the public's perspective), it may be a powerful avenue of influence for sponsors of travel.

Members who have more power, such as party leaders and committee chairs, would be the first place to look for targets of gift travel. As powerful members, it would make sense for them, ceteris paribus, to receive more invitations and to go on more gift journeys than less powerful members. Influencing members in leadership positions means influencing the legislative agenda, especially in the form of negative agenda control wherein leaders can tilt policymaking in favor of the status quo [@Cox2005]. 

Other types of member should also be better investments for sponsors who wish to provide opportunities to travel and see things outside of Washington. Members who are likely to stick around should be more attractive to sponsors for the simple reason that only members who are in office can provide reciprocal benefits to their sponsors. An advantage should therefore be given both to senior members and to members who win by large margins. 

As Alduncin, Parker, and Theriault [-@Alduncin2017] point out, senior members may also be more likely to shift their attention toward legislation and policymaking, so there may be some causation going in the other direction; that is, senior members may cultivate relationships with travel-gifting interest groups because they want to learn about policy, or they want information gains from those interest groups [@Hall2006].

In addition, because members from ideologically aligned districts, those with large margins of victory, are more likely to pursue national-level policy issues [@Grimmer2013a], we should also expect safe members to build relationships with nongovernmental groups that can provide opportunities for travel, and therefore they should take more trips at the NGOs expense.

As for the effect of members' political ideology, there is an interesting difference in how ideology may come into play in foreign travel as opposed to gift travel. [@Alduncin2017] speculate that more ideologically extreme members would tend to travel abroad less because they would be less inclined to think that they had something to learn from how foreign countries do things. For instance, Alduncin, Parker, and Theriault [-@Alduncin2017] report that conservative Republicans have always been less likely to travel (18). The authors further speculate that, because foreign travel often entails flying with members of the other party, ideologically extreme members will travel less than more moderate members.

The first speculation applies partially to gift travel because some sponsored trips are to foreign countries for the purpose of learning about social and political life abroad; other trips, however, keep members in the United States, and can bring them to ideologically charged events, such as those held by think tanks like the Heritage Foundation. Therefore, because gift travel may be more conducive to ideology-affirming experiences than foreign travel, ideological members may be no different than moderate members in their quantity of travel.

Whether or not ideological members are advantaged over moderate members depends on the sponsor organizations and their motives. If sponsors as a group are highly ideological, and they seek out likeminded legislators in order to give them information subsidies [@Hall2006], then more ideological members should travel more. Our hypothesis will remain what previous literature has found, but with the thought in mind that the sponsor-led nature of gift travel may result in different patterns than foreign travel.

The second speculation is less obviously relevant than the first to gift travel because gift travel need not be conducted as part of a group, and sponsors decide the composition of the group if there is one. Bipartisan gift travel is not unheard of, however, as there are instances, such as the entire Indiana delegation going on a trip sponsored by a soybean farmers' trade association, where members of different parties travel together, but state-delegation excursions appear to be the exception rather than the rule. Sponsors seem to hand-select which members they give to.

To reiterate the hypotheses: 1) Party leaders, chairmen, and ranking committee members will travel more (power hypothesis). 2) Safe members will travel more (safety hypothesis). 3) Senior members will travel more (seniority hypothesis). 4) Ideologically extreme members will travel less (ideology hypothesis).

Following Alduncin, Parker, and Theriault [-@Alduncin2017], we run the analyses separately for the two parties under the assumption that these explanatory variables may operate differently within each party. However, we also include whole-chamber analyses for comparison.

# Data

The data for this analysis come from the website of the Clerk of the House. The Clerk publishes yearly all of the gift travel reports filed by members of the House. This paper will analyze these reports from the 110th through the 114th Congresses (January 2007- January 2017). These data, after cleaning, collapsing duplicate trip entries, and aggregating by member consist of 2180 observations.[^2]

[^2]: Interestingly, almost half of the original entries were duplicates. For example, one of Speaker Boehner's trips to Jacksonville, Florida had 18 separate but identical filings in the 114th Congress' reports. Why this occurs is unclear, but perhaps the high rate of duplication indicates an eagerness to comply with the Rules.

<!-- After deleting all the duplicate entries, we are left with 2721 unique trips made by members during the 114th Congress. (To see if the 114th Congress was a strange session for gift travel, I checked the 113th and 112th, and these Congresses also made around 2500 trips.)

Whether this casts doubt over the accuracy of the reports is up for interpretation, but perhaps the high rate of duplication indicates an eagerness to comply with the Rules. -->

### Explanatory variables

The win percentage data were provided by Sean Theriault; the seniority, committee membership, and leadership data were gathered independently. We adjusted the win percentage observations for those members in California who ran against copartisans in the general election because of California's unique primary system. Instead of being given 100% of the vote share, Democrats who defeated other Democrats, for example, were tallied as having won with whatever percentage they got in the general election. This adjustment corrects for what may have been an overestimate of the number of unopposed members. Party and ideology (roll-call summary) data were downloaded from the voteview.org website now under the auspices of Jeff Lewis. We use the Common Space DW-NOMINATE scores that were last updated 12 December 2016: these are called *ideology* in our outputs. We also code for whether the member was part of the party controlling the House. *Majority status* is coded as 1 if the member is a member of the majority party in the chamber and 0 otherwise. In our dataset, Republicans held a majority in the House for three of the five Congresses under consideration: the 112th, 113th, and 114th Congresses. The Democrats controlled the chamber for the reamining two: the 110th and 111th Congresses. Leadership is operationalized in three different ways, and it is important that the reader be clear as to what each means. *Chairman* indicates whether the member was a committee chairman. Its converse is *committee*, which includes those who were ranking members on their committees. Finally, there is *party leader*, which captures whether the member is Speaker, majority or minority leader, a whip, or chairman of either the Republican or Democratic caucus.

### Dependent variable

We have one primary dependent variable: *trips* is a count of the number of separate journeys reported by each member to the Clerk of the House; each unique report counts as one trip. We have run the following analyses using a total count of the number of days spent traveling, and the results are substantively equivalent.

## Descriptive Statistics

After grouping all trips according to the members who went on those trips, we are left with a data set comprised of 2180 members. There are a few extra members than may be expected because some members were replaced during the course of the Congress.

### Members; or, the Travelers

Let's start with some description of the members themselves. The average number of terms, our measure of seniority, is 5.7, sd = 4.6. In other words, the average member is in about their sixth term of service. The average win percentage was about 68% with a standard deviation of 13 percentage points. A full 165 (7.5%) of the members were unopposed in their election; they won with 100% of the vote. Our dataset represent periods of both full Democratic and full Republicans majorities in Congress. And, the final Congress in our dataset (the 114th) was the largest majority the Republicans had controlled of the House since 1929 [@Bump2014].

Not all members go on gift travel, but most of them do. Of the 2180 total members, 292 (13.4%) did not go on a single trip. Similarly, 253 members (11.6%) went on exactly one, 42 (11.4%) went on two, 255 (11.7%) went on three, with 4.8 trips being the mean. Figure 1 shows a histogram of the number of trips taken by all the members. The figure is heavily right-skewed (mean = 4.8, sd = 4.7, median = 4), with only 30 members going on 20 or more trips. The member to go on the most trips, 50, was Fred Upton (MI-R), both a committee chairman and a senior member. Louise Slaughter (NY-D), another senior member in a high-ranking committee position, though in the minority party, went on zero trips during the 114th Congress.

```{r, echo = F}
library(ggplot2)
setwd("/Users/zacharymcgee/Dropbox/Gift_Travel")
giftdata <- read.csv(file = "110-114Congresses.csv", header = TRUE, stringsAsFactors = FALSE)
ggplot(data = giftdata, aes(x=trips)) + geom_histogram(color="darkblue", fill="lightblue") + theme_classic()
```

Democrats travel less often, on average, compared to Republicans (see Figure 2). The average number of trips among Democrats is 4.3, but the variance is large ($\sigma^2 = 23.7 $). Republicans, on average, go on one more trip than Democrats; their average is 5.2, but again, the variance is large ($\sigma^2 = 20.3 $).

```{r, echo = F}
library(ggplot2)
setwd("/Users/zacharymcgee/Dropbox/Gift_Travel")
giftdata <- read.csv(file = "110-114Congresses.csv", header = TRUE, stringsAsFactors = FALSE)
ggplot(data = giftdata, aes(x = trips, color = as.factor(party))) + geom_histogram(bins = 15, fill="white", alpha=0.5, position="dodge") + theme_classic()
```

<!-- Clearly the relationship between seniority and number of trips is not hard and fast, but Pearson's *r* correlations can give us a preliminary understanding of the relationships between the explanatory variables and our dependent variable, the number of gift-travel trips taken. Table 1 reports these correlations. The last two columns are the dependent variables. As can be seen in the *trips* column, more positive correlations are more closely associated with positions of power in the Congress than with seniority, ideology, or win percentage.

\begin{table}[!htbp] \centering 
  \caption{} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}} cccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & winpct & seniority & ideology & leadership & committee & chairman & trips \\ 
\hline \\[-1.8ex] 
winpct & $1$ & $0.231$ & $$-$0.055$ & $0.111$ & $0.091$ & $0.088$ & $0.063$ \\ 
seniority & $0.231$ & $1$ & $$-$0.283$ & $0.401$ & $0.383$ & $0.173$ & $0.109$ \\ 
ideology & $$-$0.055$ & $$-$0.283$ & $1$ & $$-$0.037$ & $$-$0.057$ & $0.194$ & $0.203$ \\ 
leadership & $0.111$ & $0.401$ & $$-$0.037$ & $1$ & $0.911$ & $0.663$ & $0.336$ \\ 
committee & $0.091$ & $0.383$ & $$-$0.057$ & $0.911$ & $1$ & $0.689$ & $0.290$ \\ 
chairman & $0.088$ & $0.173$ & $0.194$ & $0.663$ & $0.689$ & $1$ & $0.340$ \\ 
trips & $0.063$ & $0.109$ & $0.203$ & $0.336$ & $0.290$ & $0.340$ & $1$ \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

#### Differences in Means

Two-sample t-tests can give us a first look at the question of whether the parties differ significantly in the amount of gift travel they go on, and lend some credence to the idea that the parties should be modeled separately. The first and most basic difference to note is that Democrats on average took 4.9 trips during the 114th Congress, while Republicans went on 7.13 trips on average. This difference is highly significant (p < .01). In terms of total days traveled, those two extra trips for Republicans amounts to about 5.5 days more away from Capitol Hill. The average Republican traveled for 27.2 days, and the average Democrat was gone for 21.7 (p < .01).

Whether the differences between the parties reflect party-specific behavior or simply the benefits of being the majority party will have to await further analysis. What we can say now is that there appears to be stark differences between party leadership and the rank and file: 11 trips on average for party leaders; 6.1 trips for the rank and file (p < .05). Leaders, just like Republicans as compared to Democrats, went on five more trips than rank-and-file members, but these five trips provided almost 16 more days on the road (41 vs 24.6 days, p < .05). Interestingly, leaders and rank-and-file members do not differ on the length of the average trip, which suggests that the reason for leaders' greater total of travel days is not because they took a few very long trips, say, to foreign countries. Leaders must simply take more ordinary journeys of around three days. -->

### Sponsors; or, the Givers

It is worth pausing to observe some basic facts about the organizations behind all this gift travel: the sponsors. A glance at the list of reports quickly shows that there is not a standard or system by which members are filling out their gift-travel paperwork. The Clerk's dataset does not provide a simple answer to the question of how many unique organizations are taking advantage of gift travel because filing is left up to the members and their staffs. It it up to them to spell the name of the sponsor correctly, use the full name or an abbreviation, and, indeed, know exactly who it is that is sponsoring the trip. After attempting to correct for typos and various names for the same organization, we found that a total of about 1466 nongovernmental sources provided reimbursement for travel to members of Congress between 2007 and 2017. The true number is doubtless smaller, but it seems safe to say that at least 1000 different organizations gave at least one gift-trip in that ten-year period, which equates to about 250 organizations per Congress.

We also might wonder whether travel sponsors are egalitarian bunch, each giving roughly the same number of trips per Congress, or whether the travel-sponsor universe is characterized more by a few heavy hitters that account for the bulk of members' gift travel year after year. As it turns out, a small number of familiar names are responsible for a hefty portion of the number of trips taken each Congress. The first thing to note is that only about 4% (63 out of 1466) of the sponsoring organizations averaged at least one trip per Congress, or five total in the data set. This datum would imply that only five or six dozen organizations are taking the cost of putting members on trips as a regular part of business. The other 95% or so appear to be using gift travel only sparingly, perhaps in relation to special opportunities or changes in the information environment [@Jones2012; @Kingdon1995].

The sixty-two organizations that on average sponsored one or more trips per Congress account for 72% of the all the reported trips in our data set. That is, roughly three out of every four trips are sponsored by the same sixty-three entities. The concentration of gifting behavior among a handful of sponsors is an important descriptive fact to note. Our theoretical expectation is that more powerful members will travel more often, and if the same sponsors are doing so over and over, then this makes it likely that travel sponsors are generally well-funded and strategic, not happenstance or one-off givers.

To get some notion of who the big players are, let's look briefly at the top five gifters. The most active sponsor, by far, is an organization called the Congressional Institute, which provided travel subsidies an average of 370.8 occasions per Congress. Judging from the reports, the Congressional Institute seems to invite great numbers of members, usually around 150 of them, to places near Washington, such as Hot Springs, VA. The Institute claims to advocate for congressional reform; for example, promoting the idea of a joint committee that will propose changes to rules and procedures followed in the House and Senate.

The American Israel Education Foundation (146.0 trips per Congress), the Aspen Institute (107.4), the Heritage Foundation (88.4), and the Humpty Dumpty Institute (45.6) round out the top five. Our analysis will speak to who travels and how much, but future work should investigate whether those who travel more do so because they receive trips from a wide variety of sponsors or because they are given trips again and again by the same big organizations. 

# Models and Results

Our dependent variable is a count, i.e. a sum of binary items (traveled or did not), and it is overdispursed. Further, there is heterogeneity across individuals' probability of traveling. Therefore, we use a negative binomial regression estimated via maximum likelihood. Each member of Congress does not have an equal probability of being selected to travel by a sponsoring organization. This is especially true of party leaders or committee chairs where some members hold more power or policy expertise than rank-and-file members.

<!-- Our main model representing congressional gift travel is linear and additive. I estimate the parameters using ordinary least squares, the results of which are reported in Table 2. Starting at the top of the table, we see two variables, among both parties, that are not statistically different from zero: win percentage and seniority. These null results are surprising because previous work on foreign travel has found significant effects for vote percentage and level of seniority on the number of country-days traveled as part of a Congressional Delegation [@Alduncin2017]. -->

\begin{table}[!htbp] \centering 
  \caption{Negative Binomial Regression - Gift Travel (110th-114th Congresses)} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\\[-1.8ex] & \multicolumn{3}{c}{Count of Total Gifted Trips} \\ 
 & Full Model & Republicans & Democrats \\ 
\\[-1.8ex] & (1) & (2) & (3)\\ 
\hline \\[-1.8ex] 
 Party & 0.008$^{***}$ &  &  \\ 
  & (0.001) &  &  \\ 
  & & & \\ 
 Majority Status &  & 0.600$^{***}$ & $-$0.496$^{***}$ \\ 
  &  & (0.055) & (0.064) \\ 
  & & & \\ 
 Ideology & $-$0.558$^{***}$ & 0.207 & $-$1.849$^{***}$ \\ 
  & (0.122) & (0.121) & (0.271) \\ 
  & & & \\ 
 Win Percentage & 0.008$^{***}$ & 0.003 & 0.007$^{**}$ \\ 
  & (0.002) & (0.002) & (0.002) \\ 
  & & & \\ 
 Seniority & 0.008 & 0.005 & 0.010 \\ 
  & (0.005) & (0.006) & (0.007) \\ 
  & & & \\ 
 Chairman & 0.712$^{***}$ & 0.666$^{***}$ & 0.848$^{***}$ \\ 
  & (0.089) & (0.095) & (0.155) \\ 
  & & & \\ 
 Committee (Ranking Member) & 0.363$^{***}$ & 0.682$^{***}$ & 0.164 \\ 
  & (0.092) & (0.124) & (0.130) \\ 
  & & & \\ 
 Party Leader & 0.731$^{***}$ & 0.764$^{***}$ & 0.749$^{***}$ \\ 
  & (0.141) & (0.161) & (0.213) \\ 
  & & & \\ 
 Constant & $-$0.333 & 0.779$^{***}$ & 0.263 \\ 
  & (0.193) & (0.151) & (0.153) \\ 
  & & & \\ 
\hline \\[-1.8ex] 
Observations & 2,180 & 1,102 & 1,078 \\ 
Log Likelihood & $-$5,626.451 & $-$2,842.529 & $-$2,646.532 \\ 
$\theta$ & 1.720$^{***}$  (0.077) & 2.778$^{***}$  (0.199) & 1.537$^{***}$  (0.100) \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note: Standard errors reported in parentheses.}  & \multicolumn{3}{r}{$^{*}$p$<$0.05; $^{**}$p$<$0.01; $^{***}$p$<$0.001} \\
\end{tabular} 
\end{table}

Our full model includes members from both parties. All of the independent variables produced significant results except for seniority, which should be unsurprising given our descriptive account of the data, but weakens our support for the seniority hypothesis. Ideology was the only variable to produce a negative coefficient. Due to the structure of that variable (Republicans generally have positive scores and Democrats generally have negative scores) we can infer that Democrats may be more likely to travel than Republicans. The significant, yet tiny, party coefficient tells the same story. Our party-specific analysis will better illuminate these phenomena.

The remaining independent variables have positive and significant coefficients. Safer members tend to travel more, but only slightly. Being a party leader or a committee chair both provide large effects, suggesting they are the main drivers of increased gifted trips; in other words, these powerful members go on more trips than the average member. Being a committee's ranking member also has a positive effect on gift travel, but the effect is about half that of being the chair of the committee.

Turning to our party-specific analysis, we will first focus on the Republicans (n=1102). The largest effects, again, come from holding positions of power: party leaders, committee ranking members, and committee chairs. As hypothesized, each of these statuses increases the likelihood of taking more trips, for a given member. Being in the majority also leads to more trips; as they say, a rising tide lifts all boats. If sponsors are seeking influence from members who can get things done in a polarized Congress then targeting the most powerful members is a logical strategy. Power, in this instance, means the ability to control the rules and/or be at the table to draft bills. As regular order fades and the bill drafting process is restricted to fewer and fewer members, impacting the members who have a seat at the table will be critical for sponsoring organizations hoping to have policy influence [@Sinclair2012; @Curry2015]. We imagine if we had data going back to the mid-twentieth century, these results might look different for those Congresses.

Seniority remains statistically insignificant in the GOP model and it is now joined by ideology and win percentage in that designation. These results lead us to believe that sponsors must be less concerned about the electoral safety of members, which may suggest that they care more about short-term policy influence. With the term limits imposed on committee chairmanships, it is not shocking that sponsors may seek shorter-term influence, focusing mainly on members who have positions of power despite how long they may have served. If it is true that short-term influence is the goal, then seniority's insignificance in affecting gift travel follows this same logic. Ideology, on the other hand, is surprising. Factionalism has been prominent (most recently) within the House Republican Party with the creation of the Tea Party Caucus, following the 2010 elections. The Tea Party was followed, in turn, by the House Freedom Caucus.[^3] These factions would be easy targets for conservative think tanks for information-subsidy trips, but that does not appear to be what is going on. That being said, not all policy issues are purely ideological and, surely, all gift travel is not ideological either [@Lee2009]. <!-- Our finding here delivers initial evidence for rejecting our ideology hypothesis, at least in the context of the House Republican Party. -->

[^3]: The House Freedom Caucus formed out of former Republican Study Committee members. The Republican Study Committee originally emerged to provide a place for members to propose ideologically conservative policy ideas, and to react to the Republican leadership's insistence on compromising with Democrats in the 1970s.

Focusing now on the Democrats (n=1078), the largest effect comes from ideology--a complete reverse from our results from the Republicans. Because more liberal Democrats have negative ideology scores, the results are interpreted as more liberal Democrats being more likely to travel more often. Where we found conservatives to lack any ideological glue from gifted trips, the Democrats seem to engage in it heavily. This may be representative of an asymmetry in the underlying organizations of these two parties. If Democrats are more likely to be rewarded for concrete solutions-based governance, it might make sense that the most extreme members are actively engaging in fact-finding missions and information processing at the behest of gift-travel sponsors [@Grossman2016]. Or, it may be the case that conservatives are organizing in exactly the same way as liberal Democrats, but the conservatives' avenue for ideological travel is not official gift travel. At this point, we can only speculate because the data do not provide insight into the causes these ideological differences in gifted travel between the two parties. Ideology aside, the remaining big effects--again--come from holding positions of power. Committee chairs have larger effects than party leaders among the Democrats. Interestingly, status as a ranking member is not statistically significant. Win percentage returns as a significant factor, with a very tiny effect-size. Safer members go on marginally more gifted trips. Seniority remains insignificant.

Our most puzzling finding comes from the negative effect of being in the majority. For Democrats, being in the majority actually leads to fewer gifted trips. What we can learn from this result is that the focus of sponsors is especially narrow. That is, groups sponsoring gift travel are interested in the small group of members with power. For the rest of the majority party's members (when Democrats are in control), being in the majority actually means going on fewer trips. The explanatory variables for why these rank-and-file members are less likely to travel are probably related more to their district's geographic location, demographic features of their constituency, or policy-area expertise. It is also possible that certain trips that rank-and-file members may have been asked to attend were bumped from the trip in favor of party leaders or committee chairs, such nondecisions are difficult to measure. But, why is this a factor of the House Democratic Party and not of the House Republican Party? If ideology were an expalantory factor for the Republicans, it could be attributed to factionalism. Unfortunately, given the data we have, it is difficult to say why rank-and-file Republicans travel more often when they are in the majority, while Democrats do not.

# Conclusion

With all of our data on the table, consider how our hypotheses faired. In all three models, the power hypothesis variables did most of the explanatory work. In each model, being a party leader or committee chair led to significantly more trips than the average member. The only caveat we found was that Democratic ranking members did not have statistically significant increases in trips. Our safety hypothesis, electorally safe members would be more attractive bets for sponsoring organizations, turned out to be correct across all three models, but the effect-size was miniscule. Seniority defied our expectations and appeared insignificant in all three models. There is not a relationship between time served and number of gifted trips taken by members. Sponsoring organizations are certainly interested in targeting members with the power to impact legislation in the most meaningful ways. As the legislative process continues to centralize in the House, we can expect to see this targeting of party leaders and committee chairs by sponsors of gift travel continue.

Our ideology hypothesis, that ideologically extreme members will travel less, turned out to be wrong. In fact, liberal Democrats traveled more than moderate Democrats. There was no significant relationship between more conservative ideology and increased trips for Republicans. This is curious, as there is research indicating that some interest groups are aligned with certain parties and that such alignment is driven by policy interests [@Koger2010]. Alternatively, ideology may not matter for the GOP because of an already high degree of conservatism within the party whereas extreme liberalism is more uncommon among Democrats [@Theriault2008]. For instance, the average DW-NOMINATE score for Republicans is 0.64 while it is -0.37 for Democrats, indicating a greater distance from 0, the theoretical midpoint, for Republican members.
 
Gift travel seems like an easy way to influence factions within the parties. Despite these theoretical reasons, perhaps it is monetarily impractical to send factions or ideologically extreme members on trips that merely reinforce the members' policy views. Or, gift travel is simply not the avenue of influence. Members may pay their own way to ideological or faction-sponsored events.

The last set of findings we present addresses the role of a member's party controlling the chamber. We found that majority status increases Republican members' number of trips, but decreases Democratic members' number of trips. These results bolster our findings related to our power hypopthesis. Sponsoring organizations appear to have narrow interests when attempting to influence policy and to accomplish that goal they favor party leaders and committee chairs. For all other rank-and-file members, what affects their number of gifted trips is likely district or constituency driven. We do not currently have the data to model these explanatory factors, but this is a fertile area for future gift-travel research.

A proper continuation of Alduncin, Parker, and Theriault's work [-@Alduncin2014; -@Alduncin2017] would examine who travels with whom and how often. Using what the Clerk of the House provides, we could determine which members were visiting the same locations at the same times, and use this information to investigate how member-level attributes relate to the partisan nature of their gift-travel behavior. Many trips gifted during the Congresses analyzed here involved members traveling together, and we still have yet to find out if party polarization's effect on CODEL travel is felt also on gift travel.

Gift travel is an overlooked aspect of members' relationships with interest groups and non-governmental organizations. Many questions are still unanswered. How does gift travel change over extended periods of time? What is it good for? Researchers should appreciate the potentially important things we have to learn from this unusual form of documented lobbying and travel.

# References
